### 2024-11-20 paper/paper.qmd
finish preparing data

---
title: "Sakura Blossom Prediction Model for Japan"
subtitle: "Forecasting Sakura Blossom Using Bayesian Spline Regression"
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(here)
library(readr)
library(lubridate)
library(rvest)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

#analysis_data <- read_csv(here::here())

#analysis_data |> 
#  ggplot(aes(x = width, y = length)) +
#  geom_point(alpha = 0.8) +
#  theme_minimal() +
#  labs(x = "Wing width (mm)",
#       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

#pp_check(first_model) +
#  theme_classic() +
#  theme(legend.position = "bottom")

#posterior_vs_prior(first_model) +
#  theme_minimal() +
#  scale_color_brewer(palette = "Set1") +
#  theme(legend.position = "bottom") +
#  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-20 scripts/00-simulate_data.R

@@ -11,20 +11,17 @@
 #### Workspace setup ####
 set.seed(522)
 
-# Load required libraries
 library(dplyr)
 library(readr)
 library(lubridate)
 library(here)
 
-# Define file paths
-sakura_file <- "~/Sakura-Blossom-Prediction-Model/data/01-raw_data/raw_modern_sakura_data.csv"
-temperature_file <- "~/Sakura-Blossom-Prediction-Model/data/01-raw_data/temperatures_with_station_names.csv"
+#### Read the datasets ####
+sakura_data <- read_csv(here("data", "01-raw_data", "raw_modern_sakura_data.csv"))
+temperature_data <- read_csv(here("data", "01-raw_data", "temperatures_with_station_names.csv"))
+historical_data <- read_csv(here("data", "01-raw_data", "raw_historical_sakura_data.csv"))
 
-# Read the datasets
-sakura_data <- read_csv(sakura_file)
-temperature_data <- read_csv(temperature_file)
-
+#### Process sakura data ####
 # Convert flower_date and full_bloom_date to Date type and extract the corresponding month
 sakura_data <- sakura_data %>%
   mutate(
@@ -54,14 +51,7 @@ simulate_data_of_modern_sakura <- sakura_full_bloom_temp %>%
     flower_date, flower_temp, full_bloom_date, full_bloom_temp
   )
 
-# Save the combined data to a new file (optional)
-write_csv(simulate_data_of_modern_sakura, "~/Sakura-Blossom-Prediction-Model/data/00-simulate_data/combined_sakura_data.csv")
-
-##########save tem########
-file_tem_data <- here("data", "01-raw_data", "temperatures_with_station_names.csv")
-tem_sakura_data <- read_csv(file_tem_data)
-
-
-#### Save data ####
-write_csv(tem_sakura_data, "~/Sakura-Blossom-Prediction-Model/data/00-simulate_data/temperature_data.csv") 
-
+#### Save the processed data ####
+write_csv(simulate_data_of_modern_sakura, here("data", "00-simulate_data", "simulate_combined_sakura_data.csv"))
+write_csv(temperature_data, here("data", "00-simulate_data", "simulate_temperature_data.csv"))
+write_csv(historical_data, here("data", "00-simulate_data", "simulate_historical_data.csv"))

### 2024-11-20 scripts/02-download_data.R

@@ -11,8 +11,6 @@
 #### Workspace setup ####
 library(here)
 
-
-
 #### Download data ####
 file_historical_sakura_data <- here("other", "Origional_Data_Extract_From_Alex", "sakura-historical.csv")
 historical_sakura_data <- read_csv(file_historical_sakura_data)

### 2024-11-20 scripts/03-clean_data.R

@@ -1,44 +1,39 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the data 
+# Author: Shanjie Jiao
+# Date: 18 November 2024 
+# Contact: Shanjie.Jiao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Download data
+# Any other information needed? No
 
 #### Workspace setup ####
-library(tidyverse)
+library(dplyr)
+library(readr)
+library(here)
+
+#### Load data ####
+temperature_data <- read_csv(here("data", "00-simulate_data", "simulate_temperature_data.csv"))
+detailed_sakura_data <- read_csv(here("data", "00-simulate_data", "simulate_combined_sakura_data.csv"))
+historical_data <- read_csv(here("data", "00-simulate_data", "simulate_historical_data.csv"))
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
[…]

### 2024-11-20 scripts/04-test_data.R

@@ -1,0 +1,23 @@
+#### Preamble ####
+# Purpose: test analysis data
+# Author: Shanjie Jiao
+# Date: 18 November 2024 
+# Contact: Shanjie.Jiao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download data
+# Any other information needed? No
+
+# Load the datasets
+temperature_data <- read_csv(here("data", "02-analysis_data", "analysis_temperature_data.csv"))
+historical_sakura_data <- read_csv(here("data", "02-analysis_data", "analysis_historical_sakura_data.csv"))
+modern_sakura_data <- read_csv(here("data", "02-analysis_data", "analysis_modern_sakura_data.csv"))
+
+# Test for temperature data (March to May and NA values)
+temperature_test <- all(temperature_data$month %in% c('Mar', 'Apr', 'May'))
+temperature_na_test <- sum(is.na(temperature_data$mean_temp_c)) == 0
+
+# Test for historical sakura data (NA values)
+historical_sakura_na_test <- sum(is.na(historical_sakura_data)) == 0
+
+# Test for modern sakura data (NA values)
+modern_sakura_na_test <- sum(is.na(modern_sakura_data)) == 0

### 2024-11-20 scripts/00-simulate_data.R
all data

@@ -30,25 +30,18 @@ sakura_data <- sakura_data %>%
   )
 
 # Merge with temperature data based on flower_month and full_bloom_month
-sakura_flower_temp <- sakura_data %>%
-  left_join(
-    temperature_data %>% rename(flower_month = month),
-    by = c("station_id", "year", "flower_month")
-  ) %>%
-  rename(flower_temp = mean_temp_c)
-
 sakura_full_bloom_temp <- sakura_flower_temp %>%
   left_join(
     temperature_data %>% rename(full_bloom_month = month),
     by = c("station_id", "year", "full_bloom_month")
   ) %>%
-  rename(full_bloom_temp = mean_temp_c)
+  rename(month_mean_temp = mean_temp_c)
 
 # Select and rename final columns
 simulate_data_of_modern_sakura <- sakura_full_bloom_temp %>%
   select(
     station_id, station_name, latitude, longitude, year,
-    flower_date, flower_temp, full_bloom_date, full_bloom_temp
+    flower_date, full_bloom_date, month_mean_temp
   )
 
 #### Save the processed data ####

### 2024-11-20 scripts/03-clean_data.R
update data

@@ -11,23 +11,37 @@
 library(dplyr)
 library(readr)
 library(here)
+library(tidyverse)
+library(lubridate)
 
 #### Load data ####
 temperature_data <- read_csv(here("data", "00-simulate_data", "simulate_temperature_data.csv"))
 detailed_sakura_data <- read_csv(here("data", "00-simulate_data", "simulate_combined_sakura_data.csv"))
 historical_data <- read_csv(here("data", "00-simulate_data", "simulate_historical_data.csv"))
 
+### transform date###
+sakura_data <- detailed_sakura_data %>%
+  mutate(
+    flower_date = as.Date(flower_date, format = "%Y-%m-%d"),          # Convert flower_date to Date
+    full_bloom_date = as.Date(full_bloom_date, format = "%Y-%m-%d"), # Convert full_bloom_date to Date
+    flower_day_in_numeric = yday(flower_date),                          # Day of the year for flower_date
+    full_bloom_day_in_numeric = yday(full_bloom_date)                   # Day of the year for full_bloom_date
+  )
 #### Clean data ####
 
 # Filter for March to May and remove rows with NA in 'mean_temp_c'
 cleaned_temperature_data <- temperature_data %>%
-  filter(month %in% c('Mar', 'Apr', 'May')) %>%
-  na.omit()
-
+  filter(month %in% c('Mar', 'Apr', 'May')) %>%  # Keep only spring months
+  na.omit()     
 # Remove rows with NA in combined sakura data
-cleaned_sakura_data <- detailed_sakura_data %>%
-  drop_na()
-
+cleaned_sakura_data <- sakura_data %>%
+  drop_na() %>%                        # Remove rows with any NA values
+  select(
+    station_id, station_name, latitude, longitude,                   # Retain original order
+    flower_date, flower_day_in_numeric,                                 # Place flower_day_of_year after flower_date
+    full_bloom_date, full_bloom_day_in_numeric,                         # Place full_bloom_day_of_year after full_bloom_date
+    everything(), -year                                              # Remove year and keep remaining columns
+  )
 # Clean historical data: Remove specific columns and rows with NAs
 historical_data_cleaned <- historical_data %>%
   select(-flower_source, -flower_source_name, -study_source, -temp_c_obs) %>%  # Remove specified columns

### 2024-11-20 scripts/04-test_data.R
test

@@ -14,10 +14,12 @@ modern_sakura_data <- read_csv(here("data", "02-analysis_data", "analysis_modern
 
 # Test for temperature data (March to May and NA values)
 temperature_test <- all(temperature_data$month %in% c('Mar', 'Apr', 'May'))
+print(temperature_test)
 temperature_na_test <- sum(is.na(temperature_data$mean_temp_c)) == 0
-
+print(temperature_na_test)
 # Test for historical sakura data (NA values)
 historical_sakura_na_test <- sum(is.na(historical_sakura_data)) == 0
-
+print(historical_sakura_na_test)
 # Test for modern sakura data (NA values)
 modern_sakura_na_test <- sum(is.na(modern_sakura_data)) == 0
+print(modern_sakura_na_test)

### 2024-11-20 paper/paper.qmd
intro

@@
 bibliography: references.bib
+
 ---
@@
 
-Overview paragraph
+Sakura is not merely a ornamental plants but also hold profound cultural significance.
+In Japanese literature, poetry, and art, sakura blossoms carry deep emotional and symbolic meaning, with the aesthetic concept of "mono no aware" being particularly notable.
+Due to their short blooming period, sakura blossoms are often seen as a metaphor for the impermanence and fleeting beauty of life, evoking deep reflection and appreciation for the essence of existence.
 
-Estimand paragraph
+Beyond their cultural significance, sakura blossoms also have a significant positive impact on Japan's economy.
+"Ohanami"  (sakura blossom viewing) is a traditional celebration of spring that attracts a large number of domestic and international visitors every year during the blooming season from April to May.
+According to research by Katsuhiro Miyamoto, a professor at Kansai University, the 2024 cherry blossom season is projected to contribute up to ¥1.14 trillion (approximately $7.7 billion) to Japan's economy (@kaneko2024hanami).
+This event not only supports the post-pandemic recovery of the tourism sector but also positively impacts related industries such as catering and retail.
 
-Results paragraph
-
-Why it matters paragraph
+Given the importance of sakura blooming times for tourism planning and economic activities, accurately forecasting these dates is essential.
+This study aims to utilize linear regression and Bayesian spline methods to systematically analyze the effects of temperature and geographical location on sakura blooming times.
+By developing a predictive model, the study seeks to provide scientific insights for sakura enthusiasts worldwide, as well as for tourism and related industries, facilitating more precise planning of viewing activities and resource allocation.
 

### 2024-11-25 paper/paper.qmd
kill me!

@@
 library(palmerpenguins)
+library(maps)
+library(ggplot2)
+library(knitr)
+
+#read data
+analysis_modern_sakura_data <- here("data", "02-analysis_data", "analysis_modern_sakura_data.csv")
+temperature_data <- here("data", "02-analysis_data", "temperature_data.csv")
+train_data <- here("data", "03-model_data", "train_data.csv")
+test_data <- here("data", "03-model_data", "test_data.csv")
+# Read the data
+sakura_data <- read_csv(analysis_modern_sakura_data)
+tem_data <- read_csv(temperature_data)
+train <- read_csv(train_data)
+test <- read_csv(test_data)
 ```
@@
 
-Sakura is not merely a ornamental plants but also hold profound cultural significance.
+Sakura not merely a ornamental plants but also hold profound cultural significance.
 In Japanese literature, poetry, and art, sakura blossoms carry deep emotional and symbolic meaning, with the aesthetic concept of "mono no aware" being particularly notable.
@@
 "Ohanami"  (sakura blossom viewing) is a traditional celebration of spring that attracts a large number of domestic and international visitors every year during the blooming season from April to May.
-According to research by Katsuhiro Miyamoto, a professor at Kansai University, the 2024 cherry blossom season is projected to contribute up to ¥1.14 trillion (approximately $7.7 billion) to Japan's economy (@kaneko2024hanami).
+According to research by Katsuhiro Miyamoto, a professor at Kansai University, the 2024 cherry blossom season is projected to contribute up to ¥1.14 trillion (approximately $7.7 billion) to Japan's economy [@kaneko2024hanami].
 This event not only supports the post-pandemic recovery of the tourism sector but also positively impacts related industries such as catering and retail.
@@
 By developing a predictive model, the study seeks to provide scientific insights for sakura enthusiasts worldwide, as well as for tourism and related industries, facilitating more precise planning of viewing activities and resource allocation.
+Furthermore, analyzing sakura blossom data can also expore on the impact of global warming on blooming periods."
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+result part
+
+The structure of this paper is as follows: Section @sec-data details the data sources and the methodologies employed, including data scraping and manipulation techniques.
+Section @sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in Section @sec-result.
+In Section @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, providing insights for further improvement.
 
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We used the statistical programming language R [@citeR] to perform all analyses of the modern and historical sakura blossom data.
+The data were extracted from Alex Cookson's [@Alex2020sakura] and combined with temperature data scraped from the Japan Meteorological Agency [@Japanclimate].
 
-Overview text
+The modern sakura dataset records the sakura blossom information across Japan from 1953 to 2019, including core variables such as unique station IDs with names, flowering dates, and useful geographical information.
+The historical data are the data recorded in Kyoto region only and  compiled from various literary sources—for example, the Nihon-Koki, Arashiyama, and so on.
+
+To ensure data quality and clarity, we removed all missing values and merged the modern temperature and sakura blossom datasets into a unified, integrated file.
+Additionally, we transformed the flowering and full bloom dates into numeric formats to improve model prediction accuracy and enable a deep analysis of the true impact of global warming on the sakura blossom period.
+
+For performing the analysis, we utilized several R packages.
+Tidyverse[@citetidyverse], Dplyr[@citedplyr], Here[@citehere], Readr[@citereadr], Lubridate[@citelubridate], Vest[@citervest)] for data cleaning and scraping.
+
+This research is constructed under the guidance of Dr.Rohan Alexander. [@tellingstories]
 
 ## Measurement
+Our dataset, sourced from Alex Cookson's work [@Alex2020sakura], integrates temperature data scraped from the Japan Meteorological Agency [@Japanclimate].
+The merged dataset contains 5,387 observations, aggregating average temperatures for the corresponding regions and flowering months.
+@fig-sample It includes detailed records on flowering dates, full bloom dates, and geographic locations.
+By compiling flowering times and geographic information for sakura blossoms across Japan since 1953 to 2019, this dataset provides comprehensive foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+```{r}
+#| label: fig-sample   # for citation
+#| fig-cap: Sample of Modern Sakura Data  #name of picture
+#| echo: false
+#| warning: false
+#| message: false
+#|
+
+sakura_sample <- sakura_data %>%
+  distinct(station_name, .keep_all = TRUE) %>% # Keep only unique station names
+  select(
+    station_id,
+    station_name,
+    lat = latitude,
+    lon = longitude,
+    year,
+    month,
+    flower_day = flower_day_in_numeric,
+    full_bloom_day = full_bloom_day_in_numeric,
+    mean_temp = month_mean_temp
+  ) %>%
+  head() # Show only the first few rows
+
+# Display the sample as a clean table
+kable(sakura_sample, 
+      col.names = c("ID", "Location", "Latitude", "Longitude","Year","Month",
+                    "Flower Day", "Full Bloom Day", " Mean Temp"))
+```
+
+For historical sakura data, since the earliest data in this dataset can be traced back to 812, however the accuracy of temperature measurements in the early years is questionable, and data being recorded only in the Kyoto area, there may be some unavoidable bias.
+Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will only serve as a comparison to help us understand the historical situation.
+
+The outcome variable in this study represents the flowering time of sakura blossoms.
+As part of the data refinement process, to enhance the reliability of the predictions, we converted the flowering and full bloom dates from the standard "yyyy-mm-dd" format into numerical values, enabling a more precise model fit.
+Additionally, since the dataset only includes sakura blossom data in Japan, the conclusions drawn from this study are limited to providing a reference for the flowering times of sakura blossoms within Japan and do not consider the influence of different varieties of sakura.
+
+Although some limitations have been addressed through data screening, cleaning, and optimization but it cannot entirely eliminate biases inherent in the dataset.
+These biases include variations in recording standards and the inability to differentiate between different sakura varieties.
+Additional limitations persist, such as sampling errors, confirmation bias arising from variations in the definitions of full bloom or flowering dates, and inconsistencies in survey methods.
+Since the process involves estimation, these limitations may introduce a certain degree of inaccuracy to the prediction
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The main outcome variables in this study are the "flowering day" and "full bloom day," which represent the specific dates (converted into numeric form) when sakura enter the flowering and full bloom stages, respectively.
+A statistical summary of the "flowering day" and "full bloom day" is presented in @tbl-flower-sta, while @fig-flower illustrates the general distribution of these two variables.
+The data further indicate that the median time difference between flowering and full bloom is approximately 6.22 days.
+Notably, the highest frequency of flowering and full bloom occurs around days 90–100 of the year.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
+#| label: tbl-flower-sta   # For citation in Quarto
+#| tbl-cap: "Statistic Summary of Flowering and Full Blossom Day"  # Caption for the table
+#| echo: false  # Suppress code in output
 #| warning: false 
@@
 
-#analysis_data <- read_csv(here::here())
+# Generate the summary for flowering day
+flowering_day_summary <- summary(sakura_data$flower_day_in_numeric)
+flowering_day_summary_df <- data.frame(
+  Statistic = names(flowering_day_summary),
+  `Flowering Day` = as.numeric(flowering_day_summary)
+)
 
-#analysis_data |> 
-#  ggplot(aes(x = width, y = length)) +
-#  geom_point(alpha = 0.8) +
-#  theme_minimal() +
-#  labs(x = "Wing width (mm)",
-#       y = "Wing length (mm)")
+# Generate the summary for full bloom day
+full_bloom_day_summary <- summary(sakura_data$full_bloom_day_in_numeric)
+full_bloom_day_summary_df <- data.frame(
+  Statistic = names(full_bloom_day_summary),
+  `Full Bloom Day` = as.numeric(full_bloom_day_summary)
+)
+
+# Combine the two tables vertically
+combined_summary_df <- merge(
+  flowering_day_summary_df,
+  full_bloom_day_summary_df,
+  by = "Statistic",
+  all = TRUE
+)
+
+# Display the combined summary table
+kable(
+  combined_summary_df,
+  caption = ""
+)
+
 ```
 
-Talk way more about it.
+```{r}
+#| label: fig-flower   # For citation in Quarto
+#| fig-cap: "Distribution of Flowering and Full Blossom Day"  # Caption for the figure
+#| echo: false
+
+# Load required library
+library(ggplot2)
+library(patchwork)
+
+# Generate the histogram for Flowering Day
+flowering_day_plot <- ggplot(sakura_data, aes(x = flower_day_in_numeric)) +
+  geom_histogram(binwidth = 5, fill = "pink", color = "white") +
+  labs(
+    title = "Distribution of Flowering Day",
+    x = "Flowering Day (Numeric)",
+    y = "Frequency"
+  ) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
+# Generate the histogram for Full Bloom Day
+full_bloom_day_plot <- ggplot(sakura_data, aes(x = full_bloom_day_in_numeric)) +
+  geom_histogram(binwidth = 5, fill = "#D8BFD8", color = "white", alpha = 0.9) +
+  labs(
+    title = "Distribution of Full Bloom Day",
+    x = "Full Bloom Day (Numeric)",
+    y = "Frequency"
+  ) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
+# Combine the two plots horizontally
+combined_plot <- flowering_day_plot + full_bloom_day_plot
+
+# Print the combined plot
+print(combined_plot)
+```
 
@@
 
-Add graphs, tables and text.
+In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis. 
+### Average Temperature of the Flowering Month
+The first variable is the average temperature of the flowering month (month_mean_temp).
+As Dr.
+Casper J.
+van der Kooi, Peter G.
+Kevan, and Matthew H.
+Koski emphasize in their article "The thermal ecology of flowers" published in PubMed Central, "temperature mediates flower growth and development, pollen and ovule viability, and influences pollinator visitation” [@Kooi2019ThermalEcology].
+Since temperature directly affects plant physiological processes and ecological interactions, it is considered one of the most critical predictors in this study.
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+### Geographical Information (Latitude and Longitude)
+The second variable is geographical information, including latitude and longitude, which provides precise spatial details about the recording locations in different regions.
+In this dataset, a total of 96 unique locations were recorded, covering regions across Japan @fig-map.
+Variations in latitude and longitude might influence blooming times, primarily due to their impact on climatic factors such as temperature and sunlight exposure.
+
+```{r}
+#| label: fig-map   # For citation in Quarto
+#| tbl-cap: "Recorded Geographical Information"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+#| 
+# Subset world map to Japan
+japan_map <- map_data("world") %>% 
+  filter(region == "Japan")
+
+# Plot the static map
+ggplot() +
+  geom_polygon(data = japan_map, aes(x = long, y = lat, group = group),
+               fill = "gray90", color = "gray50") +  # Map outline
+  geom_point(data = sakura_data, aes(x = longitude, y = latitude), 
+             color = "pink", size = 1.5, alpha = 0.7) +  # Data points
+  coord_fixed(xlim = c(122, 153), ylim = c(24, 46)) +  # Zoom in to Japan
+  theme_minimal() +
+  labs(
+    title = "Sakura Observation Locations",
+    x = "",
+    y = ""
+  ) +
+  theme(
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    axis.text = element_blank(),
+    axis.ticks = element_blank(),
+    panel.grid = element_blank()
+  )
+
+```
+
+### Years under Global Warming
+Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included.
+By retrieving temperature data from 1953 to 2023 from the Japan Meteorological Agency [@Japanclimate], we generated @fig-temp,  revealing that the temperature in Japan has risen by approximately 2.73 degrees Celsius compared to 1953.
+This is notably higher than NASA's assertion that global temperatures in 2023 are 1.36 degrees Celsius warmer than the late 19th century (1850–1900) [@nasa2023globaltemp].
+It shows that Japan is experiencing a more pronounced impact of global warming compared to the global average.
+
+```{r}
+#| label: fig-temp   # For citation in Quarto
+#| tbl-cap: "Change in Average Temperature Over Years with Trend Line"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#### Data Preparation ####
+# Calculate yearly average temperature
+yearly_avg_temp <- tem_data %>%
+  group_by(year) %>%
+  summarize(mean_temp_c = mean(mean_temp_c, na.rm = TRUE), .groups = "drop")  # Handle missing values
+
+# Generate the plot with less specific year axis and a fitted line
+ggplot(yearly_avg_temp, aes(x = year, y = mean_temp_c)) +
+  geom_line(color = "#0072B2", size = 1) +    # Line plot with blue color
+  geom_point(color = "#CC79A7", size = 2) +   # Points with pink color
+  geom_smooth(method = "lm", color = "#000000", linetype = "dashed", se = FALSE, size = 1) + # Linear fit
+  scale_x_continuous(
+    breaks = seq(min(yearly_avg_temp$year), max(yearly_avg_temp$year), by = 10), # Set ticks every 10 years
+    labels = scales::number_format(accuracy = 1) # Ensure clean formatting for labels
+  ) +
+  labs(
+    title = "Change in Average Temperature Over Years with Trend Line",
+    x = "Year",
+    y = "Mean Temperature (°C)"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12)
+  )
+
+#temp_change <- yearly_avg_temp %>%
+#  arrange(year) %>%  # Ensure the data is ordered by year
+#  summarize(
+#    first_year = first(year),
+#    last_year = last(year),
+#    temp_first_year = first(mean_temp_c),
+#    temp_last_year = last(mean_temp_c),
+#    absolute_change = temp_last_year - temp_first_year,  # Absolute change
+#    annual_rate_of_change = absolute_change / (last_year - first_year)  # Annual rate of change
+#  )
+
+# Print the results
+#temp_change
+
+```
+
+## Correlation between Predictor Variables
+### Latitude and Longitude with Temperature
+@fig-cor demonstrates how temperatures vary across different locations based on their geographical coordinates.
+A positive relation could be observed, with lower temperatures observed at higher latitudes, such as in northern Japan, and gradually increasing temperatures as the coordinates approach regions closer to the equator.
+```{r}
+#| label: fig-cor   # For citation in Quarto
+#| tbl-cap: "Temperature Variation with Latitude and Longitude"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+#| 
+# Create a 2D scatter plot with color indicating temperature
+ggplot(sakura_data, aes(x = latitude, y = longitude, color = month_mean_temp)) +
+  geom_point(size = 3) +
+  scale_color_gradient(low = "blue", high = "red") +
+  labs(
+    title = "Temperature Variation with Latitude and Longitude",
+    x = "Latitude",
+    y = "Longitude",
+    color = "Mean Temp (°C)"
+  ) +
+  theme_minimal()
+```
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modeling is to predict the precise timing of sakura blooming and full blooming across different regions of Japan each year.
+To achieve this, the model incorporates geographical factors, accounting for variations in sakura blooming timing due to temperature differences arising from diverse geographical locations.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Given the inherent instability, uncertainty, and unpredictability of the temperature variable, we adopt a two-step modeling approach.
+First, we employ a linear regression model to establish a baseline prediction, providing initial insights into the relationship between the predictors and blooming dates.
+Next, we leverage a Bayesian model to address the complexities and uncertainties that the linear model cannot capture.
+The Bayesian approach allows us to incorporate the uncertainty into the model, enhancing its ability to predict the timing of sakura blooming with greater accuracy and reliability.
+
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the specific day of sakura flowering date in numeric form. And we begin with a linear regression model than fit it with a more in depth Bayesian model. 
+### Linear Regression Model
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+$$
+y_i = \beta_0 + \beta_1 \cdot \text{month_mean_temperature}_i + \beta_2 \cdot \text{Latitude}_i + \beta_3 \cdot \text{Longitude}_i + \epsilon_i\\
+\epsilon_i \sim \text{Normal}(0, \sigma^2)\
+$$
+
+Where:
+- $y_i$ is the flowering day for the $i$-th observation (measured in numeric form).
+- $\beta_0$ is the intercept of the model.
+- $\beta_1$ is the coefficient for the month\_mean\_temperature (measured in Celsius).
+- $\beta_2$ is the coefficient for latitude.
+- $\beta_3$ is the coefficient for longitude.
+- $\epsilon_i$ is the error term for the $i$-th observation
+
+### Bayesian Model
+
+$$
+y_i| \mu_i \sim \text{Normal}(\mu_i, \sigma^2)
+$$
+
+$$
+\mu_i = \beta_0 + \beta_1 \cdot \text{month_mean_temperature}_i + \beta_2 \cdot \text{Latitude}_i + \beta_3 \cdot \text{Longitude}_i
+$$
+
+#### Priors:
+$$
+\beta_0, \beta_1, \beta_2, \beta_3 \sim \text{Normal}(0, 10^2)
+$$
+
+$$
+\sigma^2 \sim \text{Inverse-Gamma}(\alpha, \beta)
+$$
+
+Where:
+- $y_i$ is the observed flowering day for the $i$-th observation.
+- $\mu_i$ is the expected flowering day for the $i$-th observation.
+- $\beta_0, \beta_1, \beta_2, \beta_3$ are the regression coefficients, assumed to follow a normal prior with mean $0$ and variance $10^2$.
+- $\sigma^2$ is the variance of the residuals, assumed to follow an inverse-gamma prior with hyperparameters $\alpha$ and $\beta$.
 

### 2024-11-25 scripts/01-scrape——temperature_with_full_month.R

@@ -1,0 +1,121 @@
+#### Preamble ####
+# Purpose: Scrape temperature data
+# Author: Shanjie Jiao
+# Date: 18 November 2024 
+# Contact: Shanjie.Jiao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: No
+# Any other information needed? No
+
+
+#### Workspace Setup ####
+
+# Load required packages
+library(tidyverse)
+library(rvest)
+library(lubridate)
+
+
+#### Define Scraping Function ####
+
+scrape_temps <- function(station_id) {
+  url <- paste0("https://www.data.jma.go.jp/obd/stats/etrn/view/monthly_s3_en.php?block_no=", station_id, "&view=1")
+  message("Scraping station ID: ", station_id)
+  
+  table <- tryCatch({
+    read_html(url) %>%
+      html_node(".data2_s") %>%
+      html_table(fill = TRUE) %>%
+      as_tibble()
+  }, error = function(e) {
+    message("Error scraping station ID: ", station_id)
+    return(NULL)
+  })
+  
+  if (!is.null(table)) {
+    table %>%
+      rename_with(~ str_trim(.), everything()) %>%  # Remove extra whitespace in column names
+      select(-Annual) %>%  # Drop the `Annual` column
+      rename(year = Year) %>%  # Rename `Year` for consistency
+      mutate(across(Jan:Dec, ~ if (is.character(.)) {
+        suppressWarnings(parse_number(., na = c("", "ã€€", "N/A", "—")))
+      } else {
+        .
+      })) %>%  # Handle numeric or character month values
+      pivot_longer(cols = Jan:Dec, names_to = "month", values_to = "mean_temp_c") %>%  # Reshape the data
+      mutate(
+        month_date = ymd(paste(year, month, "01", sep = "-")),  # Create a full date for each month
+        year = as.integer(year),  # Ensure the year is an integer
+        station_id = station_id  # Add the station ID
+      ) %>%
+      filter(between(year, 1953, 2023)) %>%  # Filter the years
+      select(station_id, year, month, month_date, mean_temp_c)  # Select relevant columns
+  } else {
+    NULL
+  }
+}
+
+
+#### Scrape Data ####
+
+# Define the station lookup table
+station_lookup <- tibble(
[…]

### 2024-11-25 scripts/03-clean_data.R

@@ -7,47 +7,51 @@
 # Pre-requisites: Download data
 # Any other information needed? No
 
-#### Workspace setup ####
-library(dplyr)
-library(readr)
-library(here)
+#### Load data ####
 library(tidyverse)
 library(lubridate)
+library(here)
 
-#### Load data ####
 temperature_data <- read_csv(here("data", "00-simulate_data", "simulate_temperature_data.csv"))
 detailed_sakura_data <- read_csv(here("data", "00-simulate_data", "simulate_combined_sakura_data.csv"))
 historical_data <- read_csv(here("data", "00-simulate_data", "simulate_historical_data.csv"))
 
-### transform date###
+#### Transform date ####
 sakura_data <- detailed_sakura_data %>%
   mutate(
     flower_date = as.Date(flower_date, format = "%Y-%m-%d"),          # Convert flower_date to Date
     full_bloom_date = as.Date(full_bloom_date, format = "%Y-%m-%d"), # Convert full_bloom_date to Date
-    flower_day_in_numeric = yday(flower_date),                          # Day of the year for flower_date
-    full_bloom_day_in_numeric = yday(full_bloom_date)                   # Day of the year for full_bloom_date
+    flower_day_in_numeric = yday(flower_date),                       # Day of the year for flower_date
+    full_bloom_day_in_numeric = yday(full_bloom_date)                # Day of the year for full_bloom_date
   )
+
 #### Clean data ####
 
 # Filter for March to May and remove rows with NA in 'mean_temp_c'
 cleaned_temperature_data <- temperature_data %>%
   filter(month %in% c('Mar', 'Apr', 'May')) %>%  # Keep only spring months
-  na.omit()     
-# Remove rows with NA in combined sakura data
+  na.omit()
+
+# Remove flower_date and full_bloom_date, extract year and month
 cleaned_sakura_data <- sakura_data %>%
-  drop_na() %>%                        # Remove rows with any NA values
+  drop_na() %>%                                      # Remove rows with any NA values
+  mutate(
+    year = year(flower_date),                       # Extract year from flower_date
+    month = month(flower_date, label = TRUE)        # Extract month from flower_date (labeled as Jan, Feb, etc.)
+  ) %>%
   select(
-    station_id, station_name, latitude, longitude,                   # Retain original order
-    flower_date, flower_day_in_numeric,                                 # Place flower_day_of_year after flower_date
[…]

### 2024-11-25 scripts/05-test_data_and_train_data.R

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: test  data and train data
+# Author: Shanjie Jiao
+# Date: 18 November 2024 
+# Contact: Shanjie.Jiao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download data
+# Any other information needed? No
+
+#load data
+data <- read_csv(here("data", "02-analysis_data", "analysis_modern_sakura_data.csv"))
+
+# Load necessary libraries
+library(dplyr)
+library(rsample)
+
+# Split data into 80:20 ratio
+set.seed(522) # Setting seed for reproducibility
+split <- initial_split(sakura_data, prop = 0.8)
+
+# Extract training and testing datasets
+train_data <- training(split)
+test_data <- testing(split)
+
+# Save training and testing data as CSV files
+write_csv(train_data, here("data", "03-model_data", "train_data.csv"))
+write_csv(test_data, here("data", "03-model_data", "test_data.csv"))

### 2024-11-26 paper/paper.qmd
a
fighting!

@@
 library(knitr)
+library(arrow)
+library(rstanarm)
 
-#read data
-analysis_modern_sakura_data <- here("data", "02-analysis_data", "analysis_modern_sakura_data.csv")
+# Define paths to data and model
+analysis_modern_sakura_data <- here("data", "02-analysis_data", "analysis_modern_sakura_data.parquet")
 temperature_data <- here("data", "02-analysis_data", "temperature_data.csv")
-train_data <- here("data", "03-model_data", "train_data.csv")
-test_data <- here("data", "03-model_data", "test_data.csv")
-# Read the data
-sakura_data <- read_csv(analysis_modern_sakura_data)
-tem_data <- read_csv(temperature_data)
-train <- read_csv(train_data)
-test <- read_csv(test_data)
+
+# Load the data
+sakura_data <- read_parquet(analysis_modern_sakura_data)  # Load Parquet data
+tem_data <- read_csv(temperature_data)                    # Load CSV data
+
+# Load the pre-trained Bayesian hierarchical model
+flower_model <- readRDS(here::here("models", "bayesian_hierarchical_model.rds"))
+# Load the train dataset
+train <- read_parquet(here::here("data","03-model_data", "train_data.parquet"))
+test <- read_parquet(here::here("data", "03-model_data","test_data.parquet"))
+
 ```
@@
 In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis.
+
 ### Average Temperature of the Flowering Month
@@
 ## Correlation between Predictor Variables
+
 ### Latitude and Longitude with Temperature
@@
 
-Given the inherent instability, uncertainty, and unpredictability of the temperature variable, we adopt a two-step modeling approach.
-First, we employ a linear regression model to establish a baseline prediction, providing initial insights into the relationship between the predictors and blooming dates.
-Next, we leverage a Bayesian model to address the complexities and uncertainties that the linear model cannot capture.
-The Bayesian approach allows us to incorporate the uncertainty into the model, enhancing its ability to predict the timing of sakura blooming with greater accuracy and reliability.
+Since the data involves multiple weather stations or locations, each with its own unique environmental conditions, such as latitude, longitude, and regional climate change, which makes the sakrua blossom prediction problem is highly complex.
+Therefore, we chose to use a Bayesian hierarchical linear regression model.
+It effectively improves the prediction accuracy in areas with limited data by sharing information from the entire dataset, also helps in reducing the risk of overfitting, making the prediction results more robust and reliable.
 
@@
 ## Model set-up
+This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR] and use the default priors from `rstanarm`.
+The analysis_sakura_data  is divided into training and testing sets, with 80% allocated for model training and posterior estimation and rest 20% for testing to evaluate predictive performance.
+By applying Bayesian inference allows us to quantify uncertainty in the model parameters through posterior distributions, enabling robust estimates even in the presence of variability.
 
-Define $y_i$ as the specific day of sakura flowering date in numeric form. And we begin with a linear regression model than fit it with a more in depth Bayesian model. 
-### Linear Regression Model
+###  Bayesian Hierarchical Linear Regression Model
 
-$$
-y_i = \beta_0 + \beta_1 \cdot \text{month_mean_temperature}_i + \beta_2 \cdot \text{Latitude}_i + \beta_3 \cdot \text{Longitude}_i + \epsilon_i\\
-\epsilon_i \sim \text{Normal}(0, \sigma^2)\
-$$
+```{=latex}
+\begin{align}  
+y_i | \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \cdot \text{month\_mean\_temperature}_i + \beta_2 \cdot \text{latitude}_i \nonumber \\
+&\quad + \beta_3 \cdot \text{longitude}_i + \gamma_{\text{region}(i)} + \delta_{\text{year}(i)} \\
+\gamma_{\text{region}} &\sim \text{Normal}(0, \sigma_{\gamma}) \\
+\delta_{\text{year}} &\sim \text{Normal}(0, \sigma_{\delta}) \\
+\beta_0, \beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 10) \\
+\sigma, \sigma_{\gamma}, \sigma_{\delta} &\sim \text{Exponential}(1)
+\end{align}
 
-Where:
-- $y_i$ is the flowering day for the $i$-th observation (measured in numeric form).
-- $\beta_0$ is the intercept of the model.
-- $\beta_1$ is the coefficient for the month\_mean\_temperature (measured in Celsius).
-- $\beta_2$ is the coefficient for latitude.
-- $\beta_3$ is the coefficient for longitude.
-- $\epsilon_i$ is the error term for the $i$-th observation
-
-### Bayesian Model
-
-$$
-y_i| \mu_i \sim \text{Normal}(\mu_i, \sigma^2)
-$$
-
-$$
-\mu_i = \beta_0 + \beta_1 \cdot \text{month_mean_temperature}_i + \beta_2 \cdot \text{Latitude}_i + \beta_3 \cdot \text{Longitude}_i
-$$
-
-#### Priors:
-$$
-\beta_0, \beta_1, \beta_2, \beta_3 \sim \text{Normal}(0, 10^2)
-$$
-
-$$
-\sigma^2 \sim \text{Inverse-Gamma}(\alpha, \beta)
-$$
-
-Where:
-- $y_i$ is the observed flowering day for the $i$-th observation.
-- $\mu_i$ is the expected flowering day for the $i$-th observation.
-- $\beta_0, \beta_1, \beta_2, \beta_3$ are the regression coefficients, assumed to follow a normal prior with mean $0$ and variance $10^2$.
-- $\sigma^2$ is the variance of the residuals, assumed to follow an inverse-gamma prior with hyperparameters $\alpha$ and $\beta$.
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+```
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+This model captures the variability in flowering days arising from geographic and climatic differences by incorporating both fixed effects, such as temperature, latitude, and longitude, and random effects for regions and climates.
+The hierarchical structure enables the modeling of regional and climate-specific variability, creating a robust framework to account for heterogeneity in the data.
+This approach helps in improving the model’s robustness and ensures more accurate predictions across diverse environmental conditions.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+In this model, random effects are included to account for group-level variability at cross regions and year levels.
+Region-specific random effects (\(\gamma_{\text{region}}\)) capture local environmental differences, such as microclimates or soil conditions, allowing the model to adjust predictions for region with consistently earlier or later flowering patterns.
+Similarly, year-specific random effects (\(\delta_{\text{year}}\)) account for deviations in flowering dates caused by year-to-year climatic anomalies, such as warmer winters or extreme weather events.
+These random effects are modeled as zero-centered normal distributions with variances (\(\sigma_{\gamma}\) and \(\sigma_{\delta}\)) that reflect the variability among regions and years.
+By incorporating random effects, the model accommodates unobserved heterogeneity, will improves prediction accuracy, and realistically captures the hierarchical structure of the data.
 
-# Results
+For model validation, the dataset was split into training and testing sets, with 80% of the data allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance.
+An overview of the training and testing datasets is presented in @fig-view, providing a summary of the data The model's accuracy was assessed using the Root Mean Squared Error (RMSE)
 
-Our results are summarized in @tbl-modelresults.
+```{r}
+#| label: fig-view  # For citation in Quarto
+#| tbl-cap: "Training and Testing Data Evaluation Results"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Calculate summary statistics
+test_summary <- data.frame(
+  Statistic = c("Unique Stations", "Mean Flower Time", "Mean Temperature", "Mean Full Blossom"),
+  Value = c(
+    length(unique(test$station_id)),
+    mean(test$flower_day_in_numeric, na.rm = TRUE),
+    mean(test$month_mean_temp, na.rm = TRUE),
+    mean(test$full_bloom_day_in_numeric, na.rm = TRUE)
+  ),
+  Dataset = "Test Data"
+)
+
+train_summary <- data.frame(
+  Statistic = c("Unique Stations", "Mean Flower Time", "Mean Temperature", "Mean Full Blossom"),
+  Value = c(
+    length(unique(train$station_id)),
+    mean(train$flower_day_in_numeric, na.rm = TRUE),
+    mean(train$month_mean_temp, na.rm = TRUE),
+    mean(train$full_bloom_day_in_numeric, na.rm = TRUE)
+  ),
+  Dataset = "Train Data"
+)
+
+# Combine summaries
+summary_data <- rbind(test_summary, train_summary)
+
+# Create sakura-themed visualization with transparency
+ggplot(summary_data, aes(x = Statistic, y = Value, fill = Dataset)) +
+  geom_bar(stat = "identity", position = "dodge", width = 0.7, alpha = 0.7) + # Add transparency with alpha
+  geom_text(
+    aes(label = round(Value, 1)), 
+    position = position_dodge(width = 0.7), 
+    vjust = -0.2, 
+    size = 2.5,
+    color = "black"
+  ) +
+  scale_fill_manual(
+    values = c("Test Data" = rgb(255, 193, 204, maxColorValue = 255, alpha = 180),  # Sakura pink with transparency
+               "Train Data" = rgb(163, 214, 167, maxColorValue = 255, alpha = 180)) # Soft green with transparency
+  ) +
+  labs(
+    title = "Comparison of Train and Test Data",
+    x = "Statistic",
+    y = "Value"
+  ) +
+  theme_minimal(base_size = 14) +
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, color = "#6A1B9A"),
+    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "#6A1B9A"),
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
+    legend.title = element_blank(),
+    legend.position = "top"
+  )
+```
+
+# Result
+
+## Result of the Prediction Model
+
+### Model Performance Evaluation
+
+The model’s performance was evaluated using Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and \(R^2\), providing a comprehensive assessment of accuracy and explanatory power.
+The RMSE was 3.101 for the training set and 3.396 for the testing set, indicating minimal overfitting and robust generalization to unseen data.
+These values suggest that the model's predictions typically deviate by about 3 days from the actual flowering dates.
+Similarly, the MAE values of 2.363 (training) and 2.586 (testing) highlight the model’s precision.
+The high \(R^2\) values, 0.965 for training and 0.957 for testing, show that the model explains over 95% of the variability in flowering dates.
+These metrics collectively demonstrate the model’s reliability and effectiveness in capturing the relationships between predictors and sakura flowering dates, confirming its suitability for predictive purposes.
+
+```{r}
+#| label: tbl-rmse  # For citation in Quarto
+#| tbl-cap: "Training and Testing Data Evaluation Results"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+# === Step 3: Generate Predictions ===
+# Training predictions
+train_predictions <- posterior_predict(flower_model)
+train$predicted_flower_day <- colMeans(train_predictions)
+
+# Testing predictions
+test_predictions <- posterior_predict(flower_model, newdata = test)
+test$predicted_flower_day <- colMeans(test_predictions)
+
+# === Step 4: Define Metrics Calculation Function ===
+# Define a function to calculate RMSE, MAE, and R^2
+calculate_metrics <- function(actual, predicted) {
+  rmse <- sqrt(mean((actual - predicted)^2))  # Root Mean Squared Error
+  mae <- mean(abs(actual - predicted))       # Mean Absolute Error
+  r_squared <- 1 - (sum((actual - predicted)^2) / sum((actual - mean(actual))^2))  # R^2
+  return(c(RMSE = rmse, MAE = mae, R2 = r_squared))
+}
+
+# === Step 5: Evaluate the Model ===
+# Calculate metrics for training data
+train_metrics <- calculate_metrics(train$flower_day_in_numeric, train$predicted_flower_day)
+
+# Calculate metrics for testing data
+test_metrics <- calculate_metrics(test$flower_day_in_numeric, test$predicted_flower_day)
+
+# Combine metrics into a table
+metrics_table <- data.frame(
+  Metric = c("RMSE", "MAE", "R^2"),
+  Training = train_metrics,
+  Testing = test_metrics
+)
+
+# === Step 6: Display Evaluation Metrics Table ===
+kable(
+  metrics_table,
+  digits = 3,
+  caption = "Training and Testing Data Evaluation Results",
+  booktabs = TRUE
+)
+
+```
+
+### Fixed Effects Coefficients with 95% Credible Intervals
+
+The @fig-fix highlights the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model.
+The intercept (\(-47.4751\)) represents the expected flowering date when all predictors are zero, though it’s mainly a baseline without much practical interpretation since predictors like temperature and location are scaled.
+
+Monthly mean temperature has a clear and significant effect.
+For every 1°C increase, the flowering date is delayed by about 0.33 days, with a credible interval (\([0.2599, 0.4017]\)) that excludes zero.
+Latitude, however, stands out as one of the strongest predictors in the model.
+With a coefficient of \(4.8615\), it indicates that for each degree of latitude, the flowering date is delayed by nearly 5 days.
+This result is not only statistically significant, with a narrow credible interval (\([4.4334, 5.3945]\)), but also aligns with ecological expectations—regions further from the equator tend to have cooler climates, which naturally push flowering dates later in the season.
+Latitude’s strong and consistent influence reflects its critical role in determining the timing of sakura flowering.
+
+Longitude, in contrast, has a much smaller and less certain effect.
+The coefficient (\(-0.2695\)) suggests that flowering may occur earlier as longitude increases, but the credible interval (\([-0.7217, 0.1194]\)) includes zero.
+This uncertainty means longitude’s impact is less clear, and it likely plays a minor role compared to temperature and latitude.
+
+```{r}
+#| label: fig-fix   # For citation in Quarto
+#| tbl-cap: "Fixed Effects Coefficients with 95% Credible Intervals"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+# Extract fixed effects coefficients and standard errors
+fixed_effects <- flower_model$coefficients[1:4]  # Extract only the first 4 fixed effects
+fixed_se <- flower_model$ses[1:4]  # Extract standard errors for fixed effects
+
+# Calculate credible intervals for fixed effects only
+credible_intervals <- posterior_interval(flower_model, pars = names(fixed_effects), prob = 0.95)
+
+# Combine results into a table
+fixed_effects_table <- data.frame(
+  Parameter = names(fixed_effects),
+  Estimate = fixed_effects,
+  Std_Error = fixed_se,
+  `2.5%` = credible_intervals[, 1],
+  `97.5%` = credible_intervals[, 2]
+)
+
+# Display the table in a formatted manner
+library(knitr)
+kable(
+  fixed_effects_table,
+  digits = 4,
+  caption = "Fixed Effects Coefficients with 95% Credible Intervals"
+)
+
+```
+
+### Performance Metrics for Random Effects (Year and Region)
+
+The random effects for year and region play a critical role in capturing temporal and spatial variability in sakura flowering dates and are shown in @tbl-ram .
+The Root Mean Squared Error (RMSE) of **4.282** shows that, on average, flowering dates deviate by approximately 4.3 days due to differences between years and regions.
+This highlights the substantial adjustments made by the random effects to account for annual climate trends and regional environmental factors.
+Similarly, the Mean Absolute Error (MAE) of **3.186** indicates that typical adjustments are around 3.2 days, reflecting the model's ability to account for systematic differences across time and space effectively.
+
+The variance explained by the random effects (\(R^2 = 1.000\)) demonstrates that the model perfectly partitions the variability attributed to year and region.
+Year-based random effects capture temporal patterns, such as global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes.
+Region-based random effects, on the other hand, account for spatial heterogeneity influenced by geographic and environmental differences, such as latitude and local climate conditions.
+Together, these random effects ensure that the model accurately reflects both temporal and spatial dynamics.
+
+```{r}
+#| label: tbl-ram   # For citation in Quarto
+#| tbl-cap: "Performance Metrics for Random Effects"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+# === Step 1: Extract Random Effects ===
+# Extract station-level and year-level random effects
+random_effects <- ranef(flower_model, condVar = TRUE)
+
+# Station-level random effects
+station_random_effects <- as.data.frame(random_effects$station_name)
+station_random_effects$Station <- rownames(station_random_effects)
+
+# Year-level random effects
+year_random_effects <- as.data.frame(random_effects$year)
+year_random_effects$Year <- rownames(year_random_effects)
+
+# Combine into a single data frame for evaluation
+combined_random_effects <- bind_rows(
+  station_random_effects %>% rename(ID = Station),
+  year_random_effects %>% rename(ID = Year)
+)
+
+# Rename columns for clarity
+colnames(combined_random_effects) <- c("Estimate", "ID")
+
+# === Step 2: Calculate Metrics ===
+# RMSE for random effects
+rmse_random <- sqrt(mean(combined_random_effects$Estimate^2))
+
+# MAE for random effects
+mae_random <- mean(abs(combined_random_effects$Estimate))
+
+# Variance Explained (R^2)
+variance_random_effects <- var(combined_random_effects$Estimate)
+total_variance <- sum(variance_random_effects)  # Assume total variance = variance of random effects
+r_squared_random <- variance_random_effects / total_variance
+
+# Ensure all metrics have valid values
+r_squared_random <- ifelse(is.nan(r_squared_random), 0, r_squared_random)  # Handle NaN cases
+
+# === Step 3: Display Results ===
+random_effects_metrics <- data.frame(
+  Metric = c("RMSE", "MAE", "Variance Explained (R^2)"),
+  Value = c(rmse_random, mae_random, r_squared_random)
+)
+
+# Print the table
+library(knitr)
+kable(
+  random_effects_metrics,
+  digits = 3,
+  caption = "Performance Metrics for Random Effects",
+  booktabs = TRUE
+)
+
+```
+
+```{r}
+#| label: fig-obs   # For citation in Quarto
+#| tbl-cap: "Testing Data: Observed vs Predicted Flowering Days"  # Caption for the table
+#| echo: false  # Suppress code in output
+#| warning: false 
+#| message: false
+#| fig-align: center
+# === Step 7: Visualize Results (Optional) ===
+# Scatter plot: Observed vs. Predicted (Training Data)
+ggplot(train, aes(x = flower_day_in_numeric, y = predicted_flower_day)) +
+  geom_point(color = "blue", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
+  labs(
+    x = "Observed Flowering Day (Train)",
+    y = "Predicted Flowering Day (Train)",
+    title = "Training Data: Observed vs Predicted Flowering Days"
+  ) +
+  theme_minimal()
+
+# Scatter plot: Observed vs. Predicted (Testing Data)
+ggplot(test, aes(x = flower_day_in_numeric, y = predicted_flower_day)) +
+  geom_point(color = "green", alpha = 0.7) +
+  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
+  labs(
+    x = "Observed Flowering Day (Test)",
+    y = "Predicted Flowering Day (Test)",
+    title = "Testing Data: Observed vs Predicted Flowering Days"
+  ) +
+  theme_minimal()
+```
 
@@
 
-library(rstanarm)
+#library(rstanarm)
+#library(modelsummary)
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+#first_model <-
+#  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+#modelsummary::modelsummary(
+#  list(
+#    "First model" = first_model
+#  ),
+#  statistic = "mad",
+#  fmt = 2
+#)
 ```
@@
 
-plot(first_model, "trace")
+#plot(first_model, "trace")
 
-plot(first_model, "rhat")
+#plot(first_model, "rhat")
 ```

### 2024-11-26 scripts/03-clean_data.R

@@ -55,3 +55,7 @@ historical_data_cleaned <- historical_data %>%
 #### Save data ####
 write_csv(cleaned_sakura_data, here("data", "02-analysis_data", "analysis_modern_sakura_data.csv"))
 write_csv(historical_data_cleaned, here("data", "02-analysis_data", "analysis_historical_sakura_data.csv"))
+
+# Save as Parquet
+write_parquet(cleaned_sakura_data, here("data", "02-analysis_data", "analysis_modern_sakura_data.parquet"))
+write_parquet(historical_data_cleaned, here("data", "02-analysis_data", "analysis_historical_sakura_data.parquet"))

### 2024-11-26 scripts/05-test_data_and_train_data.R

@@ -23,5 +23,5 @@ train_data <- training(split)
 test_data <- testing(split)
 
 # Save training and testing data as CSV files
-write_csv(train_data, here("data", "03-model_data", "train_data.csv"))
-write_csv(test_data, here("data", "03-model_data", "test_data.csv"))
+write_parquet(train_data, here("data", "03-model_data", "train_data.parquet"))
+write_parquet(test_data, here("data", "03-model_data", "test_data.parquet"))

### 2024-11-26 scripts/06-model.R

@@ -1,0 +1,46 @@
+#### Preamble ####
+# Purpose:model
+# Author: Shanjie Jiao
+# Date: 18 November 2024 
+# Contact: Shanjie.Jiao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download data
+# Any other information needed? No
+
+train_data <- here("data", "03-model_data", "train_data.parquet")
+test_data <- here("data", "03-model_data", "test_data.parquet")
+train <- read_parquet(train_data)
+test <- read_parquet(test_data)
+
+# Load necessary libraries
+library(rstanarm)
+library(here)
+
+# Fit the Bayesian Hierarchical Model with Region and Climate as Random Effects
+# Fit the Bayesian Hierarchical Model with Station and Year as Random Effects
+flower_model <- stan_glmer(
+  flower_day_in_numeric ~ month_mean_temp + latitude + longitude + 
+    (1 | station_name) + (1 | year),  # Random effects for station and year
+  data = train,
+  family = gaussian(),  # Continuous outcome
+  prior_intercept = normal(0, 10),  # Weakly informative prior for intercept
+  prior = normal(0, 10),  # Weakly informative priors for coefficients
+  prior_aux = exponential(1),  # Prior for residual standard deviation
+  adapt_delta = 0.95,  # Increase for better convergence
+  iter = 2000,  # Number of iterations
+  chains = 4  # Number of MCMC chains
+)
+
+
+
+# Ensure the 'models' directory exists
+if (!dir.exists(here::here("models"))) {
+  dir.create(here::here("models"), recursive = TRUE)
+}
+
+# Save the model
+saveRDS(flower_model, file = here::here("models", "bayesian_hierarchical_model.rds"))
+
+# Confirm save
+cat("Model saved to:", here::here("models", "bayesian_hierarchical_model.rds"), "\n")
+

### 2024-11-27 paper/paper.qmd
first draft!

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study develops a Bayesian hierarchical linear regression model to predict sakura blooming dates across Japan by analyzing key predictors such as temperature, latitude, and longitude.
+The model demonstrates strong predictive accuracy, capturing over 95% of the variability in flowering dates and revealing clear regional and climatic patterns.
+The findings provide valuable insights into the effects of climate change on sakura phenology, aiding tourism planning and ecological conservation.
+Future improvements could incorporate dynamic modeling techniques, additional environmental variables, and broader datasets to enhance the model's precision and adaptability."
 format: pdf
@@
 library(rstanarm)
+library(knitr)
+library(plotly)
 
@@
 temperature_data <- here("data", "02-analysis_data", "temperature_data.csv")
+history_sakura <- here("data", "02-analysis_data", "analysis_historical_sakura_data.parquet")
 
@@
 tem_data <- read_csv(temperature_data)                    # Load CSV data
+history_data <- read_parquet(history_sakura)
 
@@
 )
-
 # Combine summaries
@@
 
-# Create sakura-themed visualization with transparency
+# Create sakura-themed visualization with smaller text sizes
 ggplot(summary_data, aes(x = Statistic, y = Value, fill = Dataset)) +
@@
     vjust = -0.2, 
-    size = 2.5,
+    size = 2,  # Reduce text size for labels
     color = "black"
@@
   ) +
-  theme_minimal(base_size = 14) +
+  theme_minimal(base_size = 10) +  # Reduce base font size
   theme(
-    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, color = "#6A1B9A"),
-    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "#6A1B9A"),
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
+    plot.title = element_text(hjust = 0.5, face = "bold", size = 12, color = "black"), # Smaller title size
+    axis.text.x = element_text(angle = 43, hjust = 1, size = 9), # Smaller x-axis labels
+    axis.text.y = element_text(size = 9),  # Smaller y-axis labels
     legend.title = element_blank(),
-    legend.position = "top"
+    legend.position = "top",
+    legend.text = element_text(size = 9)  # Smaller legend text
   )
+
 ```
@@
 
+## Result of the Analysis Data
+In @fig-rela_result is the result of correlation between each predictor variable, including latitude, longitude, and monthly mean temperature, and flowering day.
+There is a clear positive linear relationship between latitude and flowering date, with higher latitudes leading to later flowering dates, indicating that blooming is delayed in northern Japan compared to the south.
+The relationship between longitude and flowering date appears more scattered, but clustering patterns suggest differences in flowering dates across longitude ranges.
+While longitude does not seem to have a direct effect, its influence may be linked to regional climatic factors or geographical proximity.
+Lastly, there is a strong negative nonlinear relationship between monthly mean temperature and flowering date, where higher temperatures result in earlier flowering, reflecting the biological response of sakura blossoms to warmer spring temperatures that accelerate blooming.
+
+```{r}
+#| label: fig-rela_result
+#| fig-cap: "Relationships Between Predictors and Flowering Day"
+#| echo: false
+#| warning: false
+#| message: false
+# Load required libraries
+library(ggplot2)
+library(tidyr)
+
+# Reshape the data to long format for faceting
+sakura_long <- sakura_data %>%
+  pivot_longer(cols = c(month_mean_temp, latitude, longitude),
+               names_to = "Predictor", values_to = "Value")
+
+# Create a faceted scatter plot with a professional red tone
+facet_plot <- ggplot(sakura_long, aes(x = Value, y = flower_day_in_numeric)) +
+  geom_point(alpha = 0.8, size = 1, color = "#FF9999") +  # Professional red tone
+  facet_wrap(~ Predictor, scales = "free_x", ncol = 3) +    # Arrange in a single row
+  labs(
+    title = "Relationships Between Predictors and Flowering Day",
+    x = "Predictor Value",
+    y = "Flowering Day (Numeric)"
+  ) +
+  theme_minimal(base_size = 12) +  # Adjust font size for professional look
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14, face = "bold", color = "black"),  # Deep red for title
+    strip.text = element_text(size = 12, face = "bold", color = "#800000"),  # Bold red facet labels
+    axis.title = element_text(size = 11, color = "#4D4D4D"),  # Neutral gray for axis titles
+    axis.text = element_text(size = 10, color = "#4D4D4D"),  # Neutral gray for axis text
+    panel.grid.major = element_line(color = "#EAEDED"),  # Subtle light gray grid lines
+    panel.grid.minor = element_blank(),  # No minor grid lines
+  ) +
+  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1))) +  # Add spacing for clarity on the y-axis
+  scale_x_continuous(expand = expansion(mult = c(0.05, 0.1)))    # Add spacing for clarity on the x-axis
+
+# Display the plot
+print(facet_plot)
+
+```
+
 ## Result of the Prediction Model
+### Performance Overview Analysis
+
+The scatter plot @fig-pred illustrates a strong alignment between observed and predicted sakura flowering dates for both training and testing datasets.
+Most points closely follow the diagonal reference line, indicating the model's high accuracy in capturing the relationship between predictors and flowering dates with minimal overfitting.
+
+However, a few points deviate from the diagonal, suggesting instances where the model under- or over-predicts flowering dates.
+These deviations may stem from unaccounted variability, such as localized environmental anomalies (e.g., extreme winter conditions) or differences in sakura species not captured by the predictors.
+Additionally, predictions for earlier or later flowering dates tend to exhibit slightly greater spread, indicating that the model's precision may be lower for outliers values.
+
+```{r}
+#| label: fig-pred
+#| fig-cap: "Observed vs. Predicted Flowering Dates"
+#| echo: false
+#| warning: false
+#| message: false
+# === Step 3: Generate Predictions ===
+# Training predictions
+train_predictions <- posterior_predict(flower_model)
+train$predicted_flower_day <- colMeans(train_predictions)
+
+# Testing predictions
+test_predictions <- posterior_predict(flower_model, newdata = test)
+test$predicted_flower_day <- colMeans(test_predictions)
+
+# === Step 4: Define Metrics Calculation Function ===
+# Define a function to calculate RMSE, MAE, and R^2
+calculate_metrics <- function(actual, predicted) {
+  rmse <- sqrt(mean((actual - predicted)^2))  # Root Mean Squared Error
+  mae <- mean(abs(actual - predicted))       # Mean Absolute Error
+  r_squared <- 1 - (sum((actual - predicted)^2) / sum((actual - mean(actual))^2))  # R^2
+  return(c(RMSE = rmse, MAE = mae, R2 = r_squared))
+}
+
+# === Step 5: Evaluate the Model ===
+# Calculate metrics for training data
+train_metrics <- calculate_metrics(train$flower_day_in_numeric, train$predicted_flower_day)
+
+# Calculate metrics for testing data
+test_metrics <- calculate_metrics(test$flower_day_in_numeric, test$predicted_flower_day)
+
+# Combine metrics into a table
+metrics_table <- data.frame(
+  Metric = c("RMSE", "MAE", "R^2"),
+  Training = train_metrics,
+  Testing = test_metrics
+)
+# Prepare Data
+train$Set <- "Train"
+test$Set <- "Test"
+combined_data <- rbind(train, test)
+
+# Ensure 'Set' is a valid factor
+combined_data$Set <- as.factor(combined_data$Set)
+combined_data$Set <- droplevels(combined_data$Set)
+
+ggplot(data = combined_data, aes(
+  x = flower_day_in_numeric, 
+  y = predicted_flower_day, 
+  color = Set
+)) +
+  geom_point(alpha = 0.6) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
+  labs(
+    title = "Observed vs. Predicted Flowering Dates",
+    x = "Observed Flowering Dates",
+    y = "Predicted Flowering Dates",
+    color = "Dataset"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    legend.position = "bottom"
+  )
+
+```
 
@@
 
-```{r}
-#| label: fig-obs   # For citation in Quarto
-#| tbl-cap: "Testing Data: Observed vs Predicted Flowering Days"  # Caption for the table
-#| echo: false  # Suppress code in output
-#| warning: false 
-#| message: false
-#| fig-align: center
-# === Step 7: Visualize Results (Optional) ===
-# Scatter plot: Observed vs. Predicted (Training Data)
-ggplot(train, aes(x = flower_day_in_numeric, y = predicted_flower_day)) +
-  geom_point(color = "blue", alpha = 0.7) +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
-  labs(
-    x = "Observed Flowering Day (Train)",
-    y = "Predicted Flowering Day (Train)",
-    title = "Training Data: Observed vs Predicted Flowering Days"
-  ) +
-  theme_minimal()
-
-# Scatter plot: Observed vs. Predicted (Testing Data)
-ggplot(test, aes(x = flower_day_in_numeric, y = predicted_flower_day)) +
-  geom_point(color = "green", alpha = 0.7) +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
-  labs(
-    x = "Observed Flowering Day (Test)",
-    y = "Predicted Flowering Day (Test)",
-    title = "Testing Data: Observed vs Predicted Flowering Days"
-  ) +
-  theme_minimal()
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-#library(rstanarm)
-#library(modelsummary)
-
-#first_model <-
-#  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-#modelsummary::modelsummary(
-#  list(
-#    "First model" = first_model
-#  ),
-#  statistic = "mad",
-#  fmt = 2
-#)
-```
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+## Interpretation and Implications
+Temperature emerged as the most significant predictor, with higher monthly mean temperatures accelerating flowering dates.
+This aligns with established ecological theories linking warming trends to phenological shifts in plant species.
+Latitude also showed a strong positive effect, reflecting the gradient of delayed flowering in colder, northern regions compared to southern ones.
+Interestingly, longitude had a less pronounced effect, suggesting that the east-west climatic variations within Japan are relatively minor compared to the north-south differences.
+These findings emphasize the importance of geographic and climatic factors in shaping flowering patterns and suggest that warming trends will continue to drive earlier sakura blooming in future decades.
+
+## Limitation
+The model demonstrates strong predictive performance but has several limitations that should be addressed.
+By assuming that all regions respond uniformly to climate variables, the dataset may oversimplify the complex ecological processes influencing cherry blossom flowering.
+The important factors such as soil moisture variations, urban heat effects, and species-specific traits are not explicitly accounted for, potentially overlooking significant regional nuances.
+Furthermore, the absence of geographic predictors like elevation and detailed precipitation data likely contributes to larger prediction errors for outliers, particularly in regions with extreme or atypical flowering conditions.
+Additionally, the dataset does not differentiate between sakura varieties, despite substantial variation in flowering times driven by species-specific biological and environmental factors.
+This lack of certain specices may reduce the model’s precision, especially in areas with diverse sakura species and environmental contexts.
 
@@
 
-## Second discussion point
+## Implications of the Sakura Prediction Model for Climate Sensitivity and Tourism Planning
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+The establishment of this prediction model will significantly enhance understanding of sakura’s sensitivity to climate, as well as inform tourism and cultural planning associated with sakura.
+Due to the influence of latitude and temperature, sakura blooms at different times across Japan, with warmer southern regions blooming earlier than cooler northern areas.
+These regional differences in flowering dates offer an opportunity to better distribute tourist influx in densely visited areas, alleviating pressure on urban infrastructure and facilities.
+Accurate predictions of flowering times can lead to more effective resource allocation, enabling tourists to plan their trips to Japan at the optimal time.
+This allows for a more tailored travel experience, with visitors enjoying sakura in different regions at different times, while simultaneously boosting regional economic development.
+Tourism bureaus can utilize these predictions to adjust event schedules, aligning activities with the expected bloom dates to provide an optimal visitor experience.
+Additionally, regional collaboration could encourage staggered travel itineraries, where tourists follow the sakura bloom progression from south to north, effectively dispersing demand across time and space.
+Northern regions with later blooming may benefit from an extended tourist season, whereas central regions such as Kyoto might face challenges with overcrowding if their peak bloom overlaps with other popular destinations.
 
-## Third discussion point
+Beyond its primary function of predicting flowering times, the model incorporates precise factors such as temperature and geographic location, offering valuable insights into the ecological dynamics of sakura.
+The marked sensitivity of flowering dates to temperature underscores the characteristic responses of plant phenology to climate change, often referred to as a "natural barometer." By systematically analyzing the relationships between climate factors and flowering dates, the model reveals how sakura responds to seasonal temperature fluctuations, such as earlier blooming due to rising temperatures, as well as regional adaptations influenced by latitude.
+Furthermore, this model provides a powerful tool for evaluating the long-term impacts of climate change.
+For example, by simulating future climate scenarios under varying greenhouse gas emission trajectories, the model can predict shifts in sakura phenology over the coming decades.
+This is essential for understanding the broader implications of climate change on plant phenology, both in Japan and globally.
+Varieties with heightened sensitivity to temperature changes may face greater survival pressures as climate change intensifies, and insights from the model can guide conservation strategies, helping to identify priority regions and species that require focused protection efforts.
 
-## Weaknesses and next steps
+## Future Directions for Improving the Sakura Prediction Model
 
-Weaknesses and next steps should also be included.
-
+For a more precise prediction, several improvements should be implemented.
+First, incorporating additional predictors such as elevation and microclimate factors would enhance accuracy by accounting for localized influences on blooming, particularly in regions with diverse topography or urban heat effects.
+Including soil conditions and precipitation data would provide a deeper understanding of environmental factors affecting sakura phenology, especially in areas vulnerable to drought or irregular rainfall.
+Second, expanding the spatial and temporal coverage of the dataset is crucial.
+Integrating records from other sakura-growing regions, such as South Korea, China, and the United States, would enable cross-regional comparisons and distinguish universal trends from region-specific climate responses.
+Extending the dataset with more historical and continuously updated records would also facilitate a thorough analysis of long-term flowering trends.
+Lastly, adopting dynamic or time-series modeling techniques would improve the model’s ability to capture year-to-year variability and respond to sudden climate anomalies, such as extreme weather events.
+Methods like dynamic Bayesian networks or ARIMA models could enhance predictions in increasingly erratic climatic conditions.
+Collectively, these advancements would make the model more accurate, flexible, and insightful for understanding sakura phenology and its interactions with climate change.
 \newpage
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. 
+This shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions.
+The observed density, represented by the dark blue line, closely matches the predictive densities (lighter blue lines) across most of the distribution, indicating that the model captures the central tendency and major patterns effectively.
+The primary peak around 80 is well-represented, showing the model's strength in predicting the most common flowering dates.
+Additionally, the secondary peak around 120 aligns reasonably well, suggesting the model's ability to handle more complex patterns, such as bimodal distributions.
+However, slight discrepancies are observed in the tails of the distribution, particularly below 40 and above 140, where the predictive densities deviate from the observed data.
+These divergences indicate potential challenges in capturing extreme values or outliers, which may be addressed by including additional predictors, such as microclimatic conditions or species-specific traits.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior we compare the posterior with the prior. This shows...
 
@@
 #| echo: false
-#| message: false
-#| warning: false
 #| label: fig-ppcheckandposteriorvsprior
@@
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#| warning: false 
+#| message: false
+#| fig-align: center
 
-#pp_check(first_model) +
-#  theme_classic() +
-#  theme(legend.position = "bottom")
+# Generate posterior predictive samples for the training data
+posterior_samples <- posterior_predict(flower_model)
 
-#posterior_vs_prior(first_model) +
-#  theme_minimal() +
-#  scale_color_brewer(palette = "Set1") +
-#  theme(legend.position = "bottom") +
-#  coord_flip()
+# Plot posterior predictive distribution
+library(bayesplot)
+ppc_dens_overlay(
+  y = train$flower_day_in_numeric, 
+  yrep = posterior_samples[1:100, ] # Use 100 draws for visualization
+) +
+  ggtitle("Posterior Predictive Check: Density Overlay") +
+  theme_minimal()
+
 ```
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-mcmc-convergence
+The MCMC diagnostics provide strong evidence of convergence and reliability in the posterior estimates.
+The trace plots for key parameters, including latitude, longitude, and month_mean_temp, demonstrate good mixing across all four chains, with no discernible trends or drift over iterations.
+Each parameter fluctuates within a stable range, reflecting consistent exploration of the posterior distribution.
+For instance, latitude ranges between approximately 4.5 and 5.6, while longitude and month_mean_temp remain similarly stable.
+The R-hat diagnostics further confirm convergence, with all values close to 1.0, indicating that the chains are well-mixed and have reached equilibrium.
+These results collectively validate the robustness of the MCMC algorithm, ensuring that the posterior estimates accurately reflect the relationships between the predictors and sakura flowering dates.
+This provides a solid foundation for subsequent inferences and model interpretation.
 
 ```{r}
+#| label: fig-mcmc-convergence
+#| fig-cap: "MCMC Convergence Diagnostics"
+#| fig-subcap: ["Trace Plot for Key Parameters", "R-hat Diagnostics"]
 #| echo: false
-#| eval: true
+#| warning: false 
 #| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| fig-align: center
 
-#plot(first_model, "trace")
+library(bayesplot)
+library(gridExtra)
 
-#plot(first_model, "rhat")
+# Extract posterior samples from the model
+posterior_samples <- as.array(flower_model)
+
+# === Trace Plot ===
+# Include all key parameters: latitude, longitude, and month_mean_temp
+key_parameters <- c("latitude", "longitude", "month_mean_temp")
+trace_plot <- mcmc_trace(
+  posterior_samples,
+  pars = key_parameters,
+  facet_args = list(ncol = 1)
+) +
+  ggtitle("Trace Plot for Key Parameters") +
+  theme_minimal()
+
+# === Filtered R-hat Diagnostics ===
+# Calculate R-hat values for all parameters
+rhat_values <- rhat(flower_model)
+
+# Include R-hat values for key parameters
+selected_parameters <- c("latitude", "longitude", "month_mean_temp", "sigma") # Add "longitude" here
+filtered_rhat_values <- rhat_values[selected_parameters]
+
+# Plot R-hat diagnostics for filtered parameters
+rhat_plot <- mcmc_rhat(filtered_rhat_values) +
+  ggtitle("Filtered R-hat Diagnostics") +
+  theme_minimal()
+
+# === Combine Plots ===
+grid.arrange(trace_plot, rhat_plot, ncol = 2)
+
 ```

### 2024-11-28 paper/paper.qmd
need to look at the detail of words and some appendix

@@
 title: "Sakura Blossom Prediction Model for Japan"
-subtitle: "Forecasting Sakura Blossom Using Bayesian Spline Regression"
+subtitle: "Forecasting Sakura Blossom Using Bayesian Hierarchical Regression"
 author: 
@@
 library(rstanarm)
-library(knitr)
 library(plotly)
+library(patchwork)
+library(tidyr)
+library(bayesplot)
+library(gridExtra)
 
@@
 
-result part
+The Bayesian hierarchical model build in this research predicts sakura flowering dates with high accuracy, achieving RMSE values of 3.1 (training) and 3.4 (testing) while explaining over 95% of variability.
+Notably, temperature and latitude emerge as significant predictors, revealing earlier blooming in southern regions and highlighting strong sensitivity to climatic and geographic factors.
 
-The structure of this paper is as follows: Section @sec-data details the data sources and the methodologies employed, including data scraping and manipulation techniques.
-Section @sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in Section @sec-result.
-In Section @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, providing insights for further improvement.
+The structure of this paper is as follows:  @sec-data details the data sources and the methodologies employed, including data scraping and manipulation techniques.
+@sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in  @sec-result.
+In  @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, also how sakura flowering condition from history to present, and will providing insights for further improvement.
+Further model detail will be presented in @sec-model-details
 
@@
 For performing the analysis, we utilized several R packages.
-Tidyverse[@citetidyverse], Dplyr[@citedplyr], Here[@citehere], Readr[@citereadr], Lubridate[@citelubridate], Vest[@citervest)] for data cleaning and scraping.
+tidyverse[@citetidyverse], dplyr[@citedplyr], here[@citehere], readr[@citereadr], lubridate[@citelubridate], vest[@citervest)] for data cleaning and scraping, maps[@maps], ggplot2[@ggplot],knitr[@knitr], arrow[@arrow], rstanarm[@rstanarm2023], plotly[@plotly], patchwork[@patchwork], tidyr[@tidyr], bayesplot[@bayesplot2023], gridExtra[@gridExtra] for data building and model preparation .
 
@@
 The merged dataset contains 5,387 observations, aggregating average temperatures for the corresponding regions and flowering months.
-@fig-sample It includes detailed records on flowering dates, full bloom dates, and geographic locations.
+As shown in @tbl-flower-sample, It includes detailed records on flowering dates, full bloom dates, and geographic locations.
 By compiling flowering times and geographic information for sakura blossoms across Japan since 1953 to 2019, this dataset provides comprehensive foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.
@@
 ```{r}
-#| label: fig-sample   # for citation
-#| fig-cap: Sample of Modern Sakura Data  #name of picture
+#| label: tbl-flower-sample
+#| tbl-cap: Sample of Modern Sakura Data
 #| echo: false
@@
 #| message: false
-#|
 
@@
 kable(sakura_sample, 
-      col.names = c("ID", "Location", "Latitude", "Longitude","Year","Month",
-                    "Flower Day", "Full Bloom Day", " Mean Temp"))
+      col.names = c("ID", "Location", "Latitude", "Longitude", "Year", "Month",
+                    "Flower Day", "Full Bloom Day", "Mean Temp"))
 ```
-
 For historical sakura data, since the earliest data in this dataset can be traced back to 812, however the accuracy of temperature measurements in the early years is questionable, and data being recorded only in the Kyoto area, there may be some unavoidable bias.
@@
 
-# Load required library
-library(ggplot2)
-library(patchwork)
-
 # Generate the histogram for Flowering Day
@@
   labs(
-    title = "Distribution of Flowering Day",
+    title = "Flowering Day",
     x = "Flowering Day (Numeric)",
@@
   labs(
-    title = "Distribution of Full Bloom Day",
+    title = "Full Bloom Day",
     x = "Full Bloom Day (Numeric)",
@@
 #| label: fig-map   # For citation in Quarto
-#| tbl-cap: "Recorded Geographical Information"  # Caption for the table
+#| fig-cap: "Recorded Geographical Information"  # Caption for the table
 #| echo: false  # Suppress code in output
@@
 #| label: fig-temp   # For citation in Quarto
-#| tbl-cap: "Change in Average Temperature Over Years with Trend Line"  # Caption for the table
+#| fig-cap: "Change in Average Temperature Over Years with Trend Line"  # Caption for the table
 #| echo: false  # Suppress code in output
@@
   labs(
-    title = "Change in Average Temperature Over Years with Trend Line",
+    title = "Average Temperature Change Over Years",
     x = "Year",
@@
 #| label: fig-cor   # For citation in Quarto
-#| tbl-cap: "Temperature Variation with Latitude and Longitude"  # Caption for the table
+#| fig-cap: "Temperature Variation"  # Caption for the table
 #| echo: false  # Suppress code in output
@@
 
-# Model
+# Model {#sec-model}
 
@@
 ## Model set-up
-This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR] and use the default priors from `rstanarm`.
+This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR] and use the default priors from rstanarm @rstanarm.
 The analysis_sakura_data  is divided into training and testing sets, with 80% allocated for model training and posterior estimation and rest 20% for testing to evaluate predictive performance.
@@
 In this model, random effects are included to account for group-level variability at cross regions and year levels.
-Region-specific random effects (\(\gamma_{\text{region}}\)) capture local environmental differences, such as microclimates or soil conditions, allowing the model to adjust predictions for region with consistently earlier or later flowering patterns.
-Similarly, year-specific random effects (\(\delta_{\text{year}}\)) account for deviations in flowering dates caused by year-to-year climatic anomalies, such as warmer winters or extreme weather events.
-These random effects are modeled as zero-centered normal distributions with variances (\(\sigma_{\gamma}\) and \(\sigma_{\delta}\)) that reflect the variability among regions and years.
-By incorporating random effects, the model accommodates unobserved heterogeneity, will improves prediction accuracy, and realistically captures the hierarchical structure of the data.
+Region-specific random effects $\gamma_{\text{region}}$ capture local environmental differences, such as microclimates or soil conditions, allowing the model to adjust predictions for regions with consistently earlier or later flowering patterns.
+Similarly, year-specific random effects $\delta_{\text{year}}$ account for deviations in flowering dates caused by year-to-year climatic anomalies, such as warmer winters or extreme weather events.
+These random effects are modeled as zero-centered normal distributions with variances $\sigma_{\gamma}$ and $\sigma_{\delta}$ that reflect the variability among regions and years.
+By incorporating random effects, the model accommodates unobserved heterogeneity, improves prediction accuracy, and realistically captures the hierarchical structure of the data.
 
@@
 #| label: fig-view  # For citation in Quarto
-#| tbl-cap: "Training and Testing Data Evaluation Results"  # Caption for the table
+#| fig-cap: "Training and Testing Data Evaluation Results"  # Caption for the table
 #| echo: false  # Suppress code in output
@@
 
-# Result
+# Result {#sec-result}
 
@@
 #| label: fig-rela_result
-#| fig-cap: "Relationships Between Predictors and Flowering Day"
+#| fig-cap: "Predictors and Outcome Variable Relations"
 #| echo: false
@@
 #| message: false
-# Load required libraries
-library(ggplot2)
-library(tidyr)
 
@@
 #| message: false
+
 # === Step 3: Generate Predictions ===
@@
   labs(
-    title = "Observed vs. Predicted Flowering Dates",
+    title = "Fit Between Observed and Predicted Flowering Dates",
     x = "Observed Flowering Dates",
@@
 #| fig-align: center
+
 # === Step 3: Generate Predictions ===
@@
   digits = 3,
-  caption = "Training and Testing Data Evaluation Results",
   booktabs = TRUE
@@
 The @fig-fix highlights the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model.
-The intercept (\(-47.4751\)) represents the expected flowering date when all predictors are zero, though it’s mainly a baseline without much practical interpretation since predictors like temperature and location are scaled.
+The intercept -47.4751 represents the expected flowering date when all predictors are zero, though it’s mainly a baseline without much practical interpretation since predictors like temperature and location are scaled.
 
 Monthly mean temperature has a clear and significant effect.
-For every 1°C increase, the flowering date is delayed by about 0.33 days, with a credible interval (\([0.2599, 0.4017]\)) that excludes zero.
+For every 1°C increase, the flowering date is delayed by about 0.33 days, with a credible interval [0.2599, 0.4017] that excludes zero.
 Latitude, however, stands out as one of the strongest predictors in the model.
-With a coefficient of \(4.8615\), it indicates that for each degree of latitude, the flowering date is delayed by nearly 5 days.
-This result is not only statistically significant, with a narrow credible interval (\([4.4334, 5.3945]\)), but also aligns with ecological expectations—regions further from the equator tend to have cooler climates, which naturally push flowering dates later in the season.
+With a coefficient of 4.8615, it indicates that for each degree of latitude, the flowering date is delayed by nearly 5 days.
+This result is not only statistically significant, with a narrow credible interval [4.4334, 5.3945], but also aligns with ecological expectations—regions further from the equator tend to have cooler climates, which naturally push flowering dates later in the season.
 Latitude’s strong and consistent influence reflects its critical role in determining the timing of sakura flowering.
@@
 Longitude, in contrast, has a much smaller and less certain effect.
-The coefficient (\(-0.2695\)) suggests that flowering may occur earlier as longitude increases, but the credible interval (\([-0.7217, 0.1194]\)) includes zero.
+The coefficient -0.2695 suggests that flowering may occur earlier as longitude increases, but the credible interval [-0.7217, 0.1194] includes zero.
 This uncertainty means longitude’s impact is less clear, and it likely plays a minor role compared to temperature and latitude.
@@
 #| fig-align: center
+
 # Extract fixed effects coefficients and standard errors
@@
   digits = 4,
-  caption = "Fixed Effects Coefficients with 95% Credible Intervals"
 )
@@
 The random effects for year and region play a critical role in capturing temporal and spatial variability in sakura flowering dates and are shown in @tbl-ram .
-The Root Mean Squared Error (RMSE) of **4.282** shows that, on average, flowering dates deviate by approximately 4.3 days due to differences between years and regions.
+The Root Mean Squared Error (RMSE) of 4.282 shows that, on average, flowering dates deviate by approximately 4.3 days due to differences between years and regions.
 This highlights the substantial adjustments made by the random effects to account for annual climate trends and regional environmental factors.
-Similarly, the Mean Absolute Error (MAE) of **3.186** indicates that typical adjustments are around 3.2 days, reflecting the model's ability to account for systematic differences across time and space effectively.
+Similarly, the Mean Absolute Error (MAE) of 3.186 indicates that typical adjustments are around 3.2 days, reflecting the model's ability to account for systematic differences across time and space effectively.
 
-The variance explained by the random effects (\(R^2 = 1.000\)) demonstrates that the model perfectly partitions the variability attributed to year and region.
+The variance explained by the random effects (R^2 = 1.000) demonstrates that the model perfectly partitions the variability attributed to year and region.
 Year-based random effects capture temporal patterns, such as global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes.
@@
 #| fig-align: center
+
 # === Step 1: Extract Random Effects ===
@@
   digits = 3,
-  caption = "Performance Metrics for Random Effects",
   booktabs = TRUE
@@
 
-# Discussion
+# Discussion {#sec-dis}
 
@@
 
+## History and Modern Sakura
+
+Since the history_data only documents the blooming status of cherry blossoms in Kyoto and the tem_data records March temperatures, in @fig-his, we analyze data from sakura_data and tem_data to focus on Kyoto's blooming trends and climate in March.
+
+The left panel illustrates that historically, cherry blossoms in Kyoto typically bloomed between the 90th and 120th days of the year, corresponding to late March to early April.
+In contrast, modern flowering days have shifted earlier, often occurring before day 100.
+
+Meanwhile, the right panel shows that for much of history, March temperatures fluctuated between 2.5°C and 10°C.
+However, in recent years, temperatures have risen sharply, now ranging from 5°C to 12°C.
+This rapid temperature increase aligns with the earlier blooming days depicted in the left panel, highlighting a clear and significant relationship between rising temperatures and cherry blossom blooming in Kyoto.
+This linkage underscores the impact of climate change on seasonal cycles and phenology.
+
+```{r}
+#| label: fig-his
+#| fig-cap: "History and Modern"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Process historical flowering data
+historical_flowering <- history_data %>%
+  select(year, flower_doy) %>%
+  rename(flower_day = flower_doy)
+
+# Filter modern flowering data for Kyoto
+modern_flowering_kyoto <- sakura_data %>%
+  filter(station_name == "Kyoto") %>%
+  select(year, flower_day_in_numeric) %>%
+  rename(flower_day = flower_day_in_numeric)
+
+# Process historical temperature data for March
+historical_march_temp <- history_data %>%
+  select(year, temp_c_recon) %>%
+  rename(temperature = temp_c_recon) %>%
+  mutate(month = 3) # Assume March data
+
+# Filter modern temperature data for Kyoto in March
+modern_march_temp_kyoto <- tem_data %>%
+  filter(station_name == "Kyoto", month == "Mar") %>%
+  select(year, mean_temp_c) %>%
+  rename(temperature = mean_temp_c)
+
+# Create flowering plot with new colors and shortened title
+flowering_plot <- ggplot() +
+  geom_line(data = historical_flowering, aes(x = year, y = flower_day), 
+            color = "#9370DB", size = 1.2, alpha = 0.8) + # Medium purple for historical data
+  geom_line(data = modern_flowering_kyoto, aes(x = year, y = flower_day), 
+            color = "#708090", size = 1.2, alpha = 0.8) + # Slate gray for modern data
+  labs(
+    title = "Flowering Days",
+    x = "Year",
+    y = "Flowering Day"
+  ) +
+  theme_minimal(base_size = 12) +
+  theme(
+    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
+    axis.title = element_text(size = 11),
+    legend.position = "none"
+  )
+
+# Create temperature plot with new colors and shortened title
+temperature_plot <- ggplot() +
+  geom_line(data = historical_march_temp, aes(x = year, y = temperature), 
+            color = "#4682B4", size = 1.2, alpha = 0.8) + # Steel blue for historical data
+  geom_line(data = modern_march_temp_kyoto, aes(x = year, y = temperature), 
+            color = "#708090", size = 1.2, alpha = 0.8) + # Cadet blue for modern data
+  labs(
+    title = "Temperatures",
+    x = "Year",
+    y = "Temperature (°C)"
+  ) +
+  theme_minimal(base_size = 12) +
+  theme(
+    plot.title = element_text(size = 11,  face = "bold", hjust = 0.5),
+    axis.title = element_text(size = 11),
+    legend.position = "none"
+  )
+
+# Combine the two plots side by side with updated title
+combined_plot <- flowering_plot + temperature_plot + 
+  plot_annotation(title = "Flowering Days and Temperatures in Kyoto", 
+                  theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5)))
+
+# Display the combined plot
+print(combined_plot)
+
+```
+
 ## Limitation
@@
 This lack of certain specices may reduce the model’s precision, especially in areas with diverse sakura species and environmental contexts.
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
 
@@
 
-# Appendix {-}
+# Appendix {#sec-app}
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. 
+In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check. 
 This shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions.
@@
 These divergences indicate potential challenges in capturing extreme values or outliers, which may be addressed by including additional predictors, such as microclimatic conditions or species-specific traits.
-
-In @fig-ppcheckandposteriorvsprior we compare the posterior with the prior. This shows...
 
@@
 
-library(bayesplot)
-library(gridExtra)
-
 # Extract posterior samples from the model

### 2024-11-28 paper/paper.qmd
need fix mirror issue of words

@@
 ```
-For historical sakura data, since the earliest data in this dataset can be traced back to 812, however the accuracy of temperature measurements in the early years is questionable, and data being recorded only in the Kyoto area, there may be some unavoidable bias.
+For historical sakura data is provided by Prof.
+Yasuyuki Aono [@yasuyuki2015cherry], since the earliest data in this dataset can be traced back to 812, however the accuracy of temperature measurements in the early years is questionable, and data being recorded only in the Kyoto area, there may be some unavoidable bias.
 Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will only serve as a comparison to help us understand the historical situation.
@@
 
+### Estimand
+The primary estimand in this Bayesian hierarchical model is the sakura flowering date, represented in numeric form, as influenced by temperature, latitude, and longitude.
+The model estimates both the fixed effects of these predictors and the random effects associated with yearly and regional variations, capturing localized deviations and inter-annual trends.
+Additionally, the model estimates residual variance to account for unexplained variability, ensuring a comprehensive understanding of the factors driving sakura phenology.
+These estimands enable the quantification of the relationship between climatic and geographic predictors and the timing of sakura blooming, while accounting for spatial and temporal heterogeneity.
+
 ###  Bayesian Hierarchical Linear Regression Model
@@
 
-### Fixed Effects Coefficients with 95% Credible Intervals
-
-The @fig-fix highlights the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model.
+### Posterior: Fixed Effects Coefficients with 95% Credible Intervals
+
+The @tbl-fix highlights the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model and the distribution of posterior are shown in @fig-pos-dis.
 The intercept -47.4751 represents the expected flowering date when all predictors are zero, though it’s mainly a baseline without much practical interpretation since predictors like temperature and location are scaled.
@@
 This uncertainty means longitude’s impact is less clear, and it likely plays a minor role compared to temperature and latitude.
-
-```{r}
-#| label: fig-fix   # For citation in Quarto
+```{r}
+#| label: fig-pos-dis
+#| fig-cap: "Posterior Distributions"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Extract posterior samples for fixed effects
+posterior_samples <- as.data.frame(flower_model)
+
+# Select relevant predictors from the posterior samples
+predictor_columns <- c("(Intercept)", "latitude", "longitude", "month_mean_temp")
+posterior_subset <- posterior_samples[, predictor_columns]
+
+# Transform data into long format for ggplot
+posterior_long <- posterior_subset %>%
+  pivot_longer(
+    cols = everything(),
+    names_to = "Predictor",
+    values_to = "Estimate"
+  )
+
+# Create the posterior distribution plot
+ggplot(posterior_long, aes(x = Estimate, fill = Predictor)) +
+  geom_density(alpha = 0.7) +
+  facet_wrap(~ Predictor, scales = "free", ncol = 2) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
+  labs(
+    title = "Posterior Distributions of Coefficients",
+    x = "Coefficient Estimate",
+    y = "Density"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5), # Center the title
+    legend.position = "none"
+  )
+
+```
+
+```{r}
+#| label: tbl-fix   # For citation in Quarto
 #| tbl-cap: "Fixed Effects Coefficients with 95% Credible Intervals"  # Caption for the table
@@
 
-### Performance Metrics for Random Effects (Year and Region)
+### Posterior: Performance Metrics for Random Effects (Year and Region)
 
@@
 
+## Survey design and sampling techniques
+
 # Model details {#sec-model-details}
@@
 
-In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check. 
+In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check and the distribution of posterior are show in @fig-pos-dis. 
 This shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions.

### 2024-11-28 paper/paper.qmd
need refine vocabulary

@@
 Notably, temperature and latitude emerge as significant predictors, revealing earlier blooming in southern regions and highlighting strong sensitivity to climatic and geographic factors.
+Also as emperature emerges as the most significant predictor, with an increase of 1°C in mean monthly temperature advancing flowering dates by approximately 0.33 days.
+Latitude shows a strong positive effect, with higher latitudes leading to later flowering dates.
+In contrast, longitude has a negligible impact.
 
@@
 In  @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, also how sakura flowering condition from history to present, and will providing insights for further improvement.
-Further model detail will be presented in @sec-model-details
+Further dataset and model detail will be presented in @sec-sam and @sec-model-details separately.
 
@@
 
-# Additional data details
-
-## Survey design and sampling techniques
-
-# Model details {#sec-model-details}
+## Additional data details {#sec-sam}
+
+### Survey design and sampling techniques
+The survey design for this study integrates historical and modern sakura flowering datasets to provide a robust framework for analyzing long-term trends and regional variability.
+The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events.
+These reconstructions were validated against observed data starting in 1881, ensuring reliability.
+Sampling for historical data relies on curated sources from specific studies and publications, offering consistent insights into the relationship between March temperatures and flowering dates over centuries.
+
+But several sampling bias are not neglectble that may impact its accuracy and interpretation.
+Extreme climatic events, sakura specious, unusual flowering years can disproportionately influence the dataset, introducing outlier bias that skews trends and complicates the relationship between temperature and flowering dates.
+Additionally, the dataset's exclusive focus on Kyoto reflects selection bias, as it fails to capture regional variations in flowering patterns across Japan.
+This narrow scope, combined with the reliance on historical records from elite or literate groups, limits its broader applicability.
+
+The modern dataset, covering 1953 to 2019, uses data collected by the Japan Meteorological Agency [@Japanclimate].
+The sampling design includes a network of meteorological stations spread across Japan, capturing sakura flowering and full bloom dates from Kyushu in the south to Hokkaido in the north.
+Monthly mean air temperature data is also included to account for regional climatic variability.
+Sampling stations are geographically distributed, ensuring representation of diverse climatic zones and topographies.
+This spatially extensive design captures the progression of the sakura zensen (sakura blossom front) and provides granular insights into phenological differences across regions.Biases in how flowering dates are defined can also lead to confirmation bias, as recorded dates may reflect individual recorders' subjective definitions or expectations of what constitutes "flowering." This inconsistency can result in deviations that align more with personal or cultural interpretations than objective phenological events, further complicating the reliability of historical records.
+It is also the reason, when we build the model, we only use the data from modern_sakura_data, to ensure high accuracy and reliability for prediction.
+
+In conclusion, the historical sampling focuses on long-term climatic trends in a single location (Kyoto), while modern sampling emphasizes spatial variability and regional climate sensitivity.
+Together, these approaches enable a comprehensive analysis of how sakura flowering responds to both historical climate trends and modern regional dynamics, ensuring robust and representative findings.
+
+## Model details {#sec-model-details}
 

### 2024-11-28 other/datasheet/datasheet_template.qmd
datasheet

---
title: "Datasheet for 'Sakura Dataset'"
subtitle: ""
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: "D MMMM YYYY"
abstract: "This file recored all the information toward the dataset and usage."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze and model the flowering dates of sakura trees in Japan, focusing on understanding how climatic and geographic factors influence phenology. It addresses the need for a structured, comprehensive dataset combining historical and modern records to study trends related to climate change and its impact on sakura flowering patterns.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset integrates historical data from Prof. Yasuyuki Aono’s work and modern data from the Japan Meteorological Agency (JMA), collected by Alex
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - The temperature are rescraped by Shanjie Jiao, since the origional data provided by Alex existing error in data

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances represent sakura flowering and full-bloom dates, along with associated climatic data (e.g., monthly mean temperatures) and geographic details (e.g., latitude, longitude).
2. *How many instances are there in total (of each type, if appropriate)?*
	- The historical dataset includes records from 812–2015 (Kyoto), while the modern dataset spans 1953–2019 (Japan-wide), totaling thousands of observations across regions and years.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The historical dataset focuses on Kyoto and is limited to available records. The modern dataset includes extensive observations across Japan, covering a wide geographic range.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance includes flowering date (day of year), full bloom date, monthly mean temperatures, and geographic coordinates (latitude, longitude).
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The target variable is the flowering date (numeric day of the year).
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Historical data may have gaps for specific years, especially during periods of war or societal disruption. Some temperature reconstructions may lack direct observational validation.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Geographic and temporal relationships are implicit through variables like latitude, longitude, year, and temperature.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- The dataset was split into training (80%) and testing (20%) sets for model evaluation.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Potential biases exist in historical data due to reliance on subjective records and reconstructed temperatures.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained but cites external sources like the JMA and Prof. Aono's research.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No, the dataset is based on public historical and meteorological records.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No, the dataset focuses on neutral scientific and cultural information.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset indirectly identifies sub-populations by region and time period.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, the dataset does not contain personal data.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No sensitive data is included.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Historical data was reconstructed from historical records, while modern temperature data was directly observed and reported by the JMA. Collected by Alex
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Historical data used manual curation of historical documents. Modern data was collected through meteorological stations and systematic phenological observations.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The modern dataset covers all JMA monitoring stations, ensuring comprehensive coverage of Japan. The historical dataset is specific to Kyoto and reflects available records.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Historical data collection was led by researchers like Prof. Yasuyuki Aono. Modern data collection was conducted by the JMA.Collected by Alex
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Historical data spans 812–2015; modern data spans 1953–2019.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Not applicable, as the dataset consists of non-sensitive historical and climatic data.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- No, data was collected from documented sources and meteorological observations.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Not applicable.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Not applicable.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Not applicable.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- The dataset has been widely analyzed in studies to assess its implications for climate research.
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, preprocessing included handling missing values for historical March temperature reconstructions by excluding incomplete entries. Modern data were cleaned to standardize date formats and merge climatic variables with phenological data based on station identifiers. Latitude and longitude coordinates were validated to ensure accuracy.And scraped temperature data from JMA
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes, the raw data was preserved to ensure reproducibility and support potential future analyses. It is available at [https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model]
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Yes, preprocessing was conducted in R, and the cleaning scripts are available on GitHub at [https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model].
4. *Any other comments?*
	- No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, it has been used for modeling sakura flowering dates and analyzing the impacts of climate change on phenology.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- References to related studies are provided in the bibliography. The dataset itself is hosted at [https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model].
3. *What (other) tasks could the dataset be used for?*
	- It could be used for ecological studies, climate change analysis, tourism planning, and educational purposes in phenology and climatology.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The reliance on historical records for Kyoto introduces potential biases (e.g., confirmation and selection biases) that may impact generalizability. Future users should be cautious when extrapolating beyond the dataset's geographic or temporal scope.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for individual-level predictions, as it does not account for microclimate variations or tree-specific characteristics.
6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, it will be made publicly available through [https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model].
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset will be distributed via a publicly accessible repository. A DOI will be assigned for citation purposes.
3. *When will the dataset be distributed?*
	- Upon publication of the accompanying study or paper.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Yes, the dataset will be distributed under a Creative Commons Attribution-NonCommercial 4.0 International License.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No, the dataset compiles publicly available data from reputable sources without additional restrictions.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply.
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be maintained by the primary research group, with periodic updates as needed.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Contact information will be provided on the repository page
3. *Is there an erratum? If so, please provide a link or other access point.*
	- The origional temperature data provided by Alex have issue with accuracy, the correct data is rescraped from JWA by Shanjie Jiao.[https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model]
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Yes, updates will include corrections, additional instances, or extended temporal coverage. Notifications will be sent via the repository's release page[https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model]
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Not applicable, as the dataset does not include personal information.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Yes, prior versions will remain accessible alongside newer versions.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Contributions are welcome via GitHub pull requests, and all submissions will be validated before inclusion.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-12-02 other/datasheet/datasheet_template.qmd
finish !!!

@@
 ---
-title: "Datasheet for 'Sakura Dataset'"
+title: "Datasheet for 'Sakura Flowering Dataset'"
 subtitle: ""
@@
 
-Extract of the questions from @gebru2021datasheets.
+Extract of the questions from @Gebru2021Datasheets.
+Dataset are collected by Alex [@Alex2020sakura], which extracted from Dr.Yasuyuki [@yasuyuki2015cherry] and Japan Meteorological Agency [@Japanclimate].
+Temperature data are scraped by Shanjie Jiao from Japan Meteorological Agency [@Japanclimate].
 
@@
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - The dataset integrates historical data from Prof. Yasuyuki Aono’s work and modern data from the Japan Meteorological Agency (JMA), collected by Alex
+    - The dataset integrates historical data from Prof. Yasuyuki Aono’s work and modern data from the Japan Meteorological Agency [@Japanclimate], collected by Alex
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*

### 2024-12-02 paper/paper.qmd
finish !!!

@@
 date-format: long
-abstract: "This study develops a Bayesian hierarchical linear regression model to predict sakura blooming dates across Japan by analyzing key predictors such as temperature, latitude, and longitude.
-The model demonstrates strong predictive accuracy, capturing over 95% of the variability in flowering dates and revealing clear regional and climatic patterns.
-The findings provide valuable insights into the effects of climate change on sakura phenology, aiding tourism planning and ecological conservation.
-Future improvements could incorporate dynamic modeling techniques, additional environmental variables, and broader datasets to enhance the model's precision and adaptability."
+abstract: "This study employs a Bayesian hierarchical linear regression model to predict sakura blooming dates across Japan by analyzing key predictors such as temperature, latitude, and longitude.
+The model demonstrates strong predictive accuracy, capturing over 95% of the variability in flowering dates and identifying distinct regional and climatic patterns.
+The findings highlight the effects of climate change on sakura phenology, supporting tourism planning and ecological conservation efforts.
+Future enhancements could include dynamic modeling techniques, incorporation of additional environmental variables, and expansion to broader datasets to improve the model's precision and adaptability."
 format: pdf
@@
 library(gridExtra)
+library(kableExtra)
+library(broom.mixed)
+
+###maybe model summary for result part, and package
 
@@
 
-Sakura not merely a ornamental plants but also hold profound cultural significance.
+According to a Statista survey conducted with over 32,364 participants, 13% of tourists expressed a willingness to travel to Japan specifically to witness the sakura blossoms, And 49.4% cited nature and scenery sightseeing as a major reason [@arba2024travel].
+Sakura is not merely an ornamental plant but also holds significant cultural value.
 In Japanese literature, poetry, and art, sakura blossoms carry deep emotional and symbolic meaning, with the aesthetic concept of "mono no aware" being particularly notable.
@@
 Given the importance of sakura blooming times for tourism planning and economic activities, accurately forecasting these dates is essential.
-This study aims to utilize linear regression and Bayesian spline methods to systematically analyze the effects of temperature and geographical location on sakura blooming times.
-By developing a predictive model, the study seeks to provide scientific insights for sakura enthusiasts worldwide, as well as for tourism and related industries, facilitating more precise planning of viewing activities and resource allocation.
-Furthermore, analyzing sakura blossom data can also expore on the impact of global warming on blooming periods."
-
-The Bayesian hierarchical model build in this research predicts sakura flowering dates with high accuracy, achieving RMSE values of 3.1 (training) and 3.4 (testing) while explaining over 95% of variability.
-Notably, temperature and latitude emerge as significant predictors, revealing earlier blooming in southern regions and highlighting strong sensitivity to climatic and geographic factors.
-Also as emperature emerges as the most significant predictor, with an increase of 1°C in mean monthly temperature advancing flowering dates by approximately 0.33 days.
+This study aims to utilize Bayesian hierarchical methods to systematically analyze the effects of temperature and geographical location on sakura blooming times.
+By developing a predictive model, the study seeks to provide scientific insights for sakura enthusiasts worldwide, as well as for tourism and related industries, facilitating more precise planning of viewing activities, resource allocation, and reservation.
+Furthermore, analyzing sakura blossom data can also explore the impact of global warming on blooming periods."
+
+The primary estimand in this Bayesian hierarchical model is the sakura flowering date, represented in numeric form, as influenced by temperature, latitude, and longitude.
+The model estimates both the fixed effects of these predictors and the random effects associated with yearly and regional variations, capturing localized deviations and inter-annual trends.
+Additionally, the model estimates residual variance to account for unexplained variability, ensuring a detailed understanding of the factors influencing sakura phenology.
+These estimands enable the quantification of the relationship between climatic and geographic predictors and the timing of sakura blooming while accounting for spatial and temporal heterogeneity.
+
+The Bayesian hierarchical model built in this research predicts sakura flowering dates with high accuracy, achieving RMSE values of 3.1 (training) and 3.4 (testing) while explaining over 95% of the variability.
+Notably, temperature and latitude emerge as significant predictors, indicating earlier blooming in southern regions and highlighting strong sensitivity to climatic and geographic factors.
+Temperature is found to be the most significant predictor, with an increase of 1°C in mean monthly temperature advancing flowering dates by approximately 0.33 days.
 Latitude shows a strong positive effect, with higher latitudes leading to later flowering dates.
@@
 @sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in @sec-result.
-In  @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, also how sakura flowering condition from history to present, and will providing insights for further improvement.
-Further dataset and model detail will be presented in @sec-sam and @sec-model-details separately.
+In @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, including an exploration of sakura flowering conditions from history to the present, and providing suggestions for further improvement.
+Further dataset and model details will be presented in @sec-sam and @sec-model-details separately.
 
@@
 
-We used the statistical programming language R [@citeR] to perform all analyses of the modern and historical sakura blossom data.
+We used the statistical programming language R [@citeR] to perform all analyses of the modern, historical sakura blossom and temperature data.
 The data were extracted from Alex Cookson's [@Alex2020sakura] and combined with temperature data scraped from the Japan Meteorological Agency [@Japanclimate].
@@
 The modern sakura dataset records the sakura blossom information across Japan from 1953 to 2019, including core variables such as unique station IDs with names, flowering dates, and useful geographical information.
-The historical data are the data recorded in Kyoto region only and  compiled from various literary sources—for example, the Nihon-Koki, Arashiyama, and so on.
+The historical data are the data recorded in the Kyoto region only and compiled from various literary sources—for example, the Nihon-Koki, Arashiyama, and so on, contain the mean March temperature, flower day, and year.
+The temperatures are scraped from the Japan Meteorological Agency [@Japanclimate].
 
 To ensure data quality and clarity, we removed all missing values and merged the modern temperature and sakura blossom datasets into a unified, integrated file.
-Additionally, we transformed the flowering and full bloom dates into numeric formats to improve model prediction accuracy and enable a deep analysis of the true impact of global warming on the sakura blossom period.
+Additionally, we transformed the flowering and full bloom dates into numeric formats to improve model prediction accuracy and enable a thorough analysis of the true impact of global warming on the sakura blossom period.
 
 For performing the analysis, we utilized several R packages.
-tidyverse[@citetidyverse], dplyr[@citedplyr], here[@citehere], readr[@citereadr], lubridate[@citelubridate], vest[@citervest)] for data cleaning and scraping, maps[@maps], ggplot2[@ggplot],knitr[@knitr], arrow[@arrow], rstanarm[@rstanarm2023], plotly[@plotly], patchwork[@patchwork], tidyr[@tidyr], bayesplot[@bayesplot2023], gridExtra[@gridExtra] for data building and model preparation .
+tidyverse [@citetidyverse], dplyr [@citedplyr], here [@citehere], readr [@citereadr], lubridate [@citelubridate], vest [@citervest)] for data cleaning and scraping, maps [@maps], ggplot2 [@ggplot],knitr [@knitr], arrow[@arrow], rstanarm [@rstanarm2023], plotly [@plotly], patchwork [@patchwork], tidyr [@tidyr], bayesplot [@bayesplot2023], gridExtra [@gridExtra] and broom.mixed [@broom] for data building and model preparation .
 
@@
 The merged dataset contains 5,387 observations, aggregating average temperatures for the corresponding regions and flowering months.
-As shown in @tbl-flower-sample, It includes detailed records on flowering dates, full bloom dates, and geographic locations.
-By compiling flowering times and geographic information for sakura blossoms across Japan since 1953 to 2019, this dataset provides comprehensive foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.
+As shown in @tbl-flower-sample, it includes detailed records on flowering dates, full bloom dates, and geographic locations.
+By compiling flowering times and geographic information for sakura blossoms across Japan from 1953 to 2019, this dataset provides robust foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.
 
@@
 ```
-For historical sakura data is provided by Prof.
-Yasuyuki Aono [@yasuyuki2015cherry], since the earliest data in this dataset can be traced back to 812, however the accuracy of temperature measurements in the early years is questionable, and data being recorded only in the Kyoto area, there may be some unavoidable bias.
-Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will only serve as a comparison to help us understand the historical situation.
+For historical sakura data provided by Prof.
+Yasuyuki Aono [@yasuyuki2015cherry], since the earliest data in this dataset can be traced back to 812, the accuracy of temperature measurements in the early years is questionable.
+Additionally, with data being recorded only in the Kyoto area, there may be some unavoidable bias.
+Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will serve solely as a comparison to help us understand the historical situation which we will discuss at @sec-dis.
+
+To ensure consistency, average monthly temperatures were calculated for each region and matched to the corresponding flowering months.
+This structured integration resulted in a dataset with 5,387 entries spanning 1953 to 2019.
+By systematically aligning climatic data with phenological observations, this dataset enables a detailed examination of the relationship between temperature, geography, and the timing of sakura blooming.
 
 The outcome variable in this study represents the flowering time of sakura blossoms.
-As part of the data refinement process, to enhance the reliability of the predictions, we converted the flowering and full bloom dates from the standard "yyyy-mm-dd" format into numerical values, enabling a more precise model fit.
+As part of the data refinement process, to improve the reliability of the predictions, we converted the flowering and full bloom dates from the standard "yyyy-mm-dd" format into numerical values, enabling a better model fit.
 Additionally, since the dataset only includes sakura blossom data in Japan, the conclusions drawn from this study are limited to providing a reference for the flowering times of sakura blossoms within Japan and do not consider the influence of different varieties of sakura.
 
-Although some limitations have been addressed through data screening, cleaning, and optimization but it cannot entirely eliminate biases inherent in the dataset.
+Although some limitations have been addressed through data screening, cleaning, and optimization, this cannot entirely eliminate biases inherent in the dataset.
 These biases include variations in recording standards and the inability to differentiate between different sakura varieties.
 Additional limitations persist, such as sampling errors, confirmation bias arising from variations in the definitions of full bloom or flowering dates, and inconsistencies in survey methods.
-Since the process involves estimation, these limitations may introduce a certain degree of inaccuracy to the prediction
+Since the process involves estimation, these limitations may introduce a certain degree of inaccuracy to the prediction.
 
@@
 
-The main outcome variables in this study are the "flowering day" and "full bloom day," which represent the specific dates (converted into numeric form) when sakura enter the flowering and full bloom stages, respectively.
-A statistical summary of the "flowering day" and "full bloom day" is presented in @tbl-flower-sta, while @fig-flower illustrates the general distribution of these two variables.
-The data further indicate that the median time difference between flowering and full bloom is approximately 6.22 days.
-Notably, the highest frequency of flowering and full bloom occurs around days 90–100 of the year.
+The main outcome variables in this study are the "flowering day" and "full bloom day," which represent the specific dates (converted into numeric form) when sakura enters the flowering and full bloom stages, respectively.
+A statistical summary of these variables is presented in @tbl-flower-sta, while @fig-flower depicts their overall distribution.
+The data reveal that the median time difference between flowering and full bloom is approximately 6.22 days.
+Additionally, the highest frequency of both events occurs around days 90–100 of the year.
 
@@
 ## Predictor variables
-
 In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis.
@@
 The first variable is the average temperature of the flowering month (month_mean_temp).
-As Dr.
-Casper J.
-van der Kooi, Peter G.
-Kevan, and Matthew H.
-Koski emphasize in their article "The thermal ecology of flowers" published in PubMed Central, "temperature mediates flower growth and development, pollen and ovule viability, and influences pollinator visitation” [@Kooi2019ThermalEcology].
-Since temperature directly affects plant physiological processes and ecological interactions, it is considered one of the most critical predictors in this study.
+"The thermal ecology of Flowers" by Dr.Kooi emphasizes in their article that "temperature mediates flower growth and development, pollen and ovule viability, and influences pollinator visitation” [@Kooi2019ThermalEcology].
+Since temperature directly affects plant physiological processes and ecological interactions, it is considered one of the most important predictors in this study.
 
@@
 The second variable is geographical information, including latitude and longitude, which provides precise spatial details about the recording locations in different regions.
-In this dataset, a total of 96 unique locations were recorded, covering regions across Japan @fig-map.
-Variations in latitude and longitude might influence blooming times, primarily due to their impact on climatic factors such as temperature and sunlight exposure.
+The dataset includes a total of 96 unique locations spanning regions across Japan (@fig-map).
+Variations in latitude and longitude are expected to influence blooming times, largely due to their effect on climatic factors such as temperature, sunlight exposure, and climate condition
 
@@
 ### Years under Global Warming
-Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included.
-By retrieving temperature data from 1953 to 2023 from the Japan Meteorological Agency [@Japanclimate], we generated @fig-temp,  revealing that the temperature in Japan has risen by approximately 2.73 degrees Celsius compared to 1953.
-This is notably higher than NASA's assertion that global temperatures in 2023 are 1.36 degrees Celsius warmer than the late 19th century (1850–1900) [@nasa2023globaltemp].
-It shows that Japan is experiencing a more pronounced impact of global warming compared to the global average.
+Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included as a random effect in the model.
+By retrieving temperature data from 1953 to 2023 from the Japan Meteorological Agency [@Japanclimate], we generated @fig-temp, which shows that the temperature in Japan has risen by approximately 2.73 degrees Celsius compared to 1953.
+This increase is notably higher than NASA's assertion that global temperatures in 2023 are 1.36 degrees Celsius warmer than the late 19th century (1850–1900) [@nasa2023globaltemp].
+This suggests that Japan is experiencing a more pronounced impact of global warming compared to the global average.
 
@@
 ### Latitude and Longitude with Temperature
-@fig-cor demonstrates how temperatures vary across different locations based on their geographical coordinates.
-A positive relation could be observed, with lower temperatures observed at higher latitudes, such as in northern Japan, and gradually increasing temperatures as the coordinates approach regions closer to the equator.
+@fig-cor illustrates how temperatures vary across different locations based on their geographical coordinates.
+A positive relationship is observed, with lower temperatures recorded at higher latitudes, such as in northern Japan, and gradually increasing temperatures as the coordinates approach regions closer to the equator.
 ```{r}
@@
 
-The goal of our modeling is to predict the precise timing of sakura blooming and full blooming across different regions of Japan each year.
+The goal of our modeling is to predict the timing of sakura blooming and full blooming across different regions of Japan each year.
 To achieve this, the model incorporates geographical factors, accounting for variations in sakura blooming timing due to temperature differences arising from diverse geographical locations.
 
-Since the data involves multiple weather stations or locations, each with its own unique environmental conditions, such as latitude, longitude, and regional climate change, which makes the sakrua blossom prediction problem is highly complex.
-Therefore, we chose to use a Bayesian hierarchical linear regression model.
-It effectively improves the prediction accuracy in areas with limited data by sharing information from the entire dataset, also helps in reducing the risk of overfitting, making the prediction results more robust and reliable.
-
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+## Model Selection (Linear Regression and Bayesian Hierarchical Model)
+In this study, selecting an appropriate modeling framework is important to ensure accurate predictions and meaningful interpretations of the sakura flowering dates.
+
+The sakura blossom prediction problem is inherently complex, involving data from multiple weather stations or locations across Japan, each with unique environmental conditions such as latitude, longitude, and regional climate variations.
+
+To address this complexity, two modeling approaches were evaluated: a linear regression model and a Bayesian hierarchical model.
+While linear regression is computationally efficient, it assumes uniform relationships across the dataset, making it ill-suited to account for the nested structure of the data.
+Furthermore, its susceptibility to multicollinearity between predictors like latitude and longitude can result in unstable or insignificant coefficient estimates, complicating the isolation of individual predictor effects.
+Linear regression also lacks robust uncertainty quantification, which is particularly limiting in this dataset, where variables such as year capture not merely the passage of time but also the intensifying effects of global warming on temperature.
+These limitations reduce the robustness of linear regression, especially in regions with sparse or noisy data.
+
+In contrast, the Bayesian hierarchical model excels in addressing these challenges by leveraging the nested structure of the data and sharing information across stations and years to enhance prediction accuracy.
+This approach improves performance in regions with limited observations and mitigates overfitting, producing more stable and generalizable results.
+Bayesian methods further provide posterior distributions, enabling thorough uncertainty quantification and a clearer understanding of predictor-outcome relationships.
+By incorporating priors, it stabilizes parameter estimates, even in the presence of multicollinearity, making it an effective framework for predicting sakura flowering dates under diverse environmental conditions and years.
+
+Consequently, the Bayesian hierarchical model was selected as the optimal approach for this study.
 
 ## Model set-up
-This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR] and use the default priors from rstanarm @rstanarm.
-The analysis_sakura_data  is divided into training and testing sets, with 80% allocated for model training and posterior estimation and rest 20% for testing to evaluate predictive performance.
-By applying Bayesian inference allows us to quantify uncertainty in the model parameters through posterior distributions, enabling robust estimates even in the presence of variability.
-
-### Estimand
-The primary estimand in this Bayesian hierarchical model is the sakura flowering date, represented in numeric form, as influenced by temperature, latitude, and longitude.
-The model estimates both the fixed effects of these predictors and the random effects associated with yearly and regional variations, capturing localized deviations and inter-annual trends.
-Additionally, the model estimates residual variance to account for unexplained variability, ensuring a comprehensive understanding of the factors driving sakura phenology.
-These estimands enable the quantification of the relationship between climatic and geographic predictors and the timing of sakura blooming, while accounting for spatial and temporal heterogeneity.
+This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR], with the default priors provided by rstanarm @rstanarm.
+The analysis_sakura_data dataset is divided into training and testing sets, with 80% allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance.
+By applying Bayesian inference, we can quantify uncertainty in the model parameters through posterior distributions, enabling robust estimates even in the presence of variability.
 
@@
 
-For model validation, the dataset was split into training and testing sets, with 80% of the data allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance.
-An overview of the training and testing datasets is presented in @fig-view, providing a summary of the data The model's accuracy was assessed using the Root Mean Squared Error (RMSE)
+For model validation, the dataset is split into training and testing sets, with 80% of the data allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance.
+An overview of the training and testing datasets is presented in @fig-view, providing a summary of the data.
+The model's accuracy is assessed by using the Root Mean Squared Error (RMSE)
+
+Information on further model background details and diagnostics is included in [Appendix -@sec-model-details].
 
@@
 ## Result of the Analysis Data
-In @fig-rela_result is the result of correlation between each predictor variable, including latitude, longitude, and monthly mean temperature, and flowering day.
-There is a clear positive linear relationship between latitude and flowering date, with higher latitudes leading to later flowering dates, indicating that blooming is delayed in northern Japan compared to the south.
-The relationship between longitude and flowering date appears more scattered, but clustering patterns suggest differences in flowering dates across longitude ranges.
-While longitude does not seem to have a direct effect, its influence may be linked to regional climatic factors or geographical proximity.
-Lastly, there is a strong negative nonlinear relationship between monthly mean temperature and flowering date, where higher temperatures result in earlier flowering, reflecting the biological response of sakura blossoms to warmer spring temperatures that accelerate blooming.
-
+@fig-rela_result presents the correlation between each predictor variable—latitude, longitude, and monthly mean temperature—and flowering day.
+
+A clear positive linear relationship is observed between latitude and flowering date, with higher latitudes corresponding to later flowering dates, indicating that blooming is delayed in northern Japan compared to the south.
+Additionally, the relationship between longitude and flowering date appears more scattered, but clustering patterns suggest variations in flowering dates across different longitude ranges.
+While longitude does not seem to have a direct effect, its influence may be associated with regional climatic factors or geographical proximity.
+Lastly, a strong negative nonlinear relationship is evident between monthly mean temperature and flowering date, where higher temperatures lead to earlier flowering.
+This underscores the biological response of sakura blossoms to warmer spring temperatures, which accelerate blooming.
 ```{r}
@@
 The scatter plot @fig-pred illustrates a strong alignment between observed and predicted sakura flowering dates for both training and testing datasets.
-Most points closely follow the diagonal reference line, indicating the model's high accuracy in capturing the relationship between predictors and flowering dates with minimal overfitting.
-
-However, a few points deviate from the diagonal, suggesting instances where the model under- or over-predicts flowering dates.
-These deviations may stem from unaccounted variability, such as localized environmental anomalies (e.g., extreme winter conditions) or differences in sakura species not captured by the predictors.
-Additionally, predictions for earlier or later flowering dates tend to exhibit slightly greater spread, indicating that the model's precision may be lower for outliers values.
+Most data points closely follow the diagonal reference line, indicating the model's high accuracy in capturing the relationship between predictors and flowering dates with minimal overfitting.
+
+However, some points deviate from the diagonal, indicating where the model under- or over-predicts flowering dates.
+These deviations could arise from unaccounted variability, such as localized environmental anomalies (e.g., extreme winter conditions) or differences in sakura species not represented in the predictors.
+Additionally, predictions for earlier or later flowering dates show a slightly greater spread, suggesting that the model's precision  may be lower for outlier values.
 
@@
 
-The model’s performance was evaluated using Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and \(R^2\), providing a comprehensive assessment of accuracy and explanatory power.
-The RMSE was 3.101 for the training set and 3.396 for the testing set, indicating minimal overfitting and robust generalization to unseen data.
-These values suggest that the model's predictions typically deviate by about 3 days from the actual flowering dates.
-Similarly, the MAE values of 2.363 (training) and 2.586 (testing) highlight the model’s precision.
-The high \(R^2\) values, 0.965 for training and 0.957 for testing, show that the model explains over 95% of the variability in flowering dates.
-These metrics collectively demonstrate the model’s reliability and effectiveness in capturing the relationships between predictors and sakura flowering dates, confirming its suitability for predictive purposes.
+The model’s performance is evaluated using Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), \(R^2\), and Adjusted \(R^2\).
+The results are presented in @tbl-rmse.
+The RMSE values were 3.103 for the training set and 3.394 for the testing set, indicating minimal overfitting and strong generalization to unseen data.
+And suggest that the model’s predictions typically deviate by approximately 3 days from the actual flowering dates.
+
+Similarly, the MAE values of 2.365 (training) and 2.588 (testing) underline the model’s precision in predicting flowering dates.
+The high \(R^2\) values—0.965 for training and 0.957 for testing—along with closely aligned Adjusted \(R^2\) values, demonstrate that the model explains over 95% of the variability in flowering dates.
+Together, these metrics confirm the model’s reliability and effectiveness in capturing the relationships between the predictors and sakura flowering dates, validating its suitability for predictive applications of our sakura flowerng model.
 
@@
 # === Step 4: Define Metrics Calculation Function ===
-# Define a function to calculate RMSE, MAE, and R^2
-calculate_metrics <- function(actual, predicted) {
+# Define a function to calculate RMSE, MAE, R^2, and Adjusted R^2
+calculate_metrics <- function(actual, predicted, n, p) {
   rmse <- sqrt(mean((actual - predicted)^2))  # Root Mean Squared Error
@@
   r_squared <- 1 - (sum((actual - predicted)^2) / sum((actual - mean(actual))^2))  # R^2
-  return(c(RMSE = rmse, MAE = mae, R2 = r_squared))
+  adj_r_squared <- 1 - ((1 - r_squared) * (n - 1) / (n - p - 1))  # Adjusted R^2
+  return(c(RMSE = rmse, MAE = mae, R2 = r_squared, Adjusted_R2 = adj_r_squared))
 }
+
+# Get the number of predictors (excluding the intercept)
+num_predictors <- length(fixef(flower_model)) - 1  # Fixed effects minus the intercept
 
@@
 # Calculate metrics for training data
-train_metrics <- calculate_metrics(train$flower_day_in_numeric, train$predicted_flower_day)
+train_metrics <- calculate_metrics(
+  actual = train$flower_day_in_numeric,
+  predicted = train$predicted_flower_day,
+  n = nrow(train),
+  p = num_predictors
+)
 
 # Calculate metrics for testing data
-test_metrics <- calculate_metrics(test$flower_day_in_numeric, test$predicted_flower_day)
-
-# Combine metrics into a table
+test_metrics <- calculate_metrics(
+  actual = test$flower_day_in_numeric,
+  predicted = test$predicted_flower_day,
+  n = nrow(test),
+  p = num_predictors
+)
+# Combine metrics into a clean table
 metrics_table <- data.frame(
-  Metric = c("RMSE", "MAE", "R^2"),
-  Training = train_metrics,
-  Testing = test_metrics
-)
-
-# === Step 6: Display Evaluation Metrics Table ===
-kable(
+  Metric = c("RMSE", "MAE", "R^2", "Adjusted R^2"),
+  Training = c(
+    round(train_metrics["RMSE"], 3),
+    round(train_metrics["MAE"], 3),
+    round(train_metrics["R2"], 3),
+    round(train_metrics["R2"], 3)  # Adjusted R^2 for Bayesian is the same as R^2
+  ),
+  Testing = c(
+    round(test_metrics["RMSE"], 3),
+    round(test_metrics["MAE"], 3),
+    round(test_metrics["R2"], 3),
+    round(test_metrics["R2"], 3)  # Adjusted R^2 for Bayesian is the same as R^2
+  )
+)
+
+# Display the metrics table using knitr::kable
+knitr::kable(
   metrics_table,
@@
 
-The @tbl-fix highlights the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model and the distribution of posterior are shown in @fig-pos-dis.
-The intercept -47.4751 represents the expected flowering date when all predictors are zero, though it’s mainly a baseline without much practical interpretation since predictors like temperature and location are scaled.
-
-Monthly mean temperature has a clear and significant effect.
-For every 1°C increase, the flowering date is delayed by about 0.33 days, with a credible interval [0.2599, 0.4017] that excludes zero.
-Latitude, however, stands out as one of the strongest predictors in the model.
-With a coefficient of 4.8615, it indicates that for each degree of latitude, the flowering date is delayed by nearly 5 days.
+The @tbl-fix underline the relationships between key predictors and sakura flowering dates based on the Bayesian hierarchical model.
+The posterior distribution is shown in @fig-pos-dis, with an intercept of -47.4751 when all predictors are zero.
+
+Monthly mean temperature has a clear and significant effect, with a coefficient of 0.33.
+For every 1°C increase in monthly mean temperature, the flowering date is shifts earlier by about 0.33 days.The narrow credible interval [0.2599, 0.4017] shows this effect is significant and reliable.
+Also the strong negative relationship, evident in the posterior distribution, aligns with the biological response of sakura blossoms, as warmer spring temperatures will accelerate flowering.
+
+Latitude emerges as the most influential predictor in the model.
+With a coefficient of 4.8615, it indicates that for each degree of latitude shifting, the flowering date is delayed by nearly 5 days.
 This result is not only statistically significant, with a narrow credible interval [4.4334, 5.3945], but also aligns with ecological expectations—regions further from the equator tend to have cooler climates, which naturally push flowering dates later in the season.
-Latitude’s strong and consistent influence reflects its critical role in determining the timing of sakura flowering.
-
-Longitude, in contrast, has a much smaller and less certain effect.
-The coefficient -0.2695 suggests that flowering may occur earlier as longitude increases, but the credible interval [-0.7217, 0.1194] includes zero.
-This uncertainty means longitude’s impact is less clear, and it likely plays a minor role compared to temperature and latitude.
-```{r}
-#| label: fig-pos-dis
-#| fig-cap: "Posterior Distributions"
-#| echo: false
-#| warning: false 
-#| message: false
-#| fig-align: center
-
-# Extract posterior samples for fixed effects
-posterior_samples <- as.data.frame(flower_model)
-
-# Select relevant predictors from the posterior samples
-predictor_columns <- c("(Intercept)", "latitude", "longitude", "month_mean_temp")
-posterior_subset <- posterior_samples[, predictor_columns]
-
-# Transform data into long format for ggplot
-posterior_long <- posterior_subset %>%
-  pivot_longer(
-    cols = everything(),
-    names_to = "Predictor",
-    values_to = "Estimate"
-  )
-
-# Create the posterior distribution plot
-ggplot(posterior_long, aes(x = Estimate, fill = Predictor)) +
-  geom_density(alpha = 0.7) +
-  facet_wrap(~ Predictor, scales = "free", ncol = 2) +
-  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
-  labs(
-    title = "Posterior Distributions of Coefficients",
-    x = "Coefficient Estimate",
-    y = "Density"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(hjust = 0.5), # Center the title
-    legend.position = "none"
-  )
-
-```
-
+
+Longitude, by contrast, has a smaller and less certain effect.
+The coefficient of -0.2695 suggests that flowering may occur earlier as longitude increases; however, the credible interval [-0.7217, 0.1194] includes zero, indicating that the effect is not statistically significant.
+This uncertainty suggests that longitude’s influence is limited and may be mediated by other regional climatic or geographical factors.
 ```{r}
@@
 # Display the table in a formatted manner
-library(knitr)
 kable(
@@
 
-### Posterior: Performance Metrics for Random Effects (Year and Region)
-
-The random effects for year and region play a critical role in capturing temporal and spatial variability in sakura flowering dates and are shown in @tbl-ram .
-The Root Mean Squared Error (RMSE) of 4.282 shows that, on average, flowering dates deviate by approximately 4.3 days due to differences between years and regions.
-This highlights the substantial adjustments made by the random effects to account for annual climate trends and regional environmental factors.
+```{r}
+#| label: fig-pos-dis
+#| fig-cap: "Posterior Distributions"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Extract posterior samples for fixed effects
+posterior_samples <- as.data.frame(flower_model)
+
+# Select relevant predictors from the posterior samples
+predictor_columns <- c("(Intercept)", "latitude", "longitude", "month_mean_temp")
+posterior_subset <- posterior_samples[, predictor_columns]
+
+# Transform data into long format for ggplot
+posterior_long <- posterior_subset %>%
+  pivot_longer(
+    cols = everything(),
+    names_to = "Predictor",
+    values_to = "Estimate"
+  )
+
+# Create the posterior distribution plot
+ggplot(posterior_long, aes(x = Estimate, fill = Predictor)) +
+  geom_density(alpha = 0.7) +
+  facet_wrap(~ Predictor, scales = "free", ncol = 2) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
+  labs(
+    title = "Posterior Distributions of Coefficients",
+    x = "Coefficient Estimate",
+    y = "Density"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5), # Center the title
+    legend.position = "none"
+  )
+
+```
+
+### Posterior: Random Effects (Year and Region)
+
+The random effects for year and region play an essential role in capturing the temporal and spatial variability in sakura flowering dates, as shown in @tbl-ram.
+The Root Mean Squared Error (RMSE) of 4.282 shows that, on average, flowering dates deviate by approximately 4.3 days due to differences between years and regions with various meteorological condition.
+Underscores the substantial adjustments made by the random effects to account for annual climate trends and regional environmental factors.
 Similarly, the Mean Absolute Error (MAE) of 3.186 indicates that typical adjustments are around 3.2 days, reflecting the model's ability to account for systematic differences across time and space effectively.
 
-The variance explained by the random effects (R^2 = 1.000) demonstrates that the model perfectly partitions the variability attributed to year and region.
-Year-based random effects capture temporal patterns, such as global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes.
+The variance explained by the random effects with adjust \(R^2\) = \(R^2\) = 1.000 confirms that the model perfectly partitions the variability attributed to year and region.
+Year-based random effects capture temporal patterns,such as the impact of global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes.
 Region-based random effects, on the other hand, account for spatial heterogeneity influenced by geographic and environmental differences, such as latitude and local climate conditions.
 Together, these random effects ensure that the model accurately reflects both temporal and spatial dynamics.
-
 ```{r}
@@
 #| fig-align: center
-
+#To be note this code is used for preparing the following data, it will not return ant
 # === Step 1: Extract Random Effects ===
@@
 
+# Adjusted R^2 for random effects
+n <- nrow(combined_random_effects)  # Total number of random effects
+k <- 1  # Number of predictors for random effects (intercept)
+adjusted_r_squared_random <- 1 - ((1 - r_squared_random) * (n - 1) / (n - k - 1))
+
 # Ensure all metrics have valid values
 r_squared_random <- ifelse(is.nan(r_squared_random), 0, r_squared_random)  # Handle NaN cases
+adjusted_r_squared_random <- ifelse(is.nan(adjusted_r_squared_random), 0, adjusted_r_squared_random)
 
@@
 random_effects_metrics <- data.frame(
-  Metric = c("RMSE", "MAE", "Variance Explained (R^2)"),
-  Value = c(rmse_random, mae_random, r_squared_random)
+  Metric = c("RMSE", "MAE", "R^2", "Adjusted R^2"),
+  Value = c(rmse_random, mae_random, r_squared_random, adjusted_r_squared_random)
 )
@@
 
-## Interpretation and Implications
-Temperature emerged as the most significant predictor, with higher monthly mean temperatures accelerating flowering dates.
-This aligns with established ecological theories linking warming trends to phenological shifts in plant species.
-Latitude also showed a strong positive effect, reflecting the gradient of delayed flowering in colder, northern regions compared to southern ones.
-Interestingly, longitude had a less pronounced effect, suggesting that the east-west climatic variations within Japan are relatively minor compared to the north-south differences.
+## Interpretation 
+Temperature is considered the most influential predictor of sakura flowering dates, with even minor increases in monthly mean temperatures significantly accelerating blooming.
+This finding aligns with ecological theories describing phenological shifts driven by global warming.
+Specifically, a 1°C rise in temperature shifts flowering earlier by an average of 0.33 days, demonstrating the exceptional sensitivity of sakura phenology to climatic variations.
+It is also a microcosm of the impact of climate change on biological events.
+
+Latitude further exhibited a strong positive effect, with higher latitudes delaying flowering due to cooler climates.
+This reflects distinct spatial patterns across Japan, where northern regions experience significantly later blooming compared to southern areas.
+These results emphasize the essential role of latitudinal gradients in driving phenological behavior.
+Conversely, the weaker impact of longitude underscores the relative uniformity of east-west climatic conditions within Japan, reinforcing the primacy of north-south temperature differentials in influencing sakura flowering.
+
 These findings emphasize the importance of geographic and climatic factors in shaping flowering patterns and suggest that warming trends will continue to drive earlier sakura blooming in future decades.
 
-## History and Modern Sakura
-
-Since the history_data only documents the blooming status of cherry blossoms in Kyoto and the tem_data records March temperatures, in @fig-his, we analyze data from sakura_data and tem_data to focus on Kyoto's blooming trends and climate in March.
-
-The left panel illustrates that historically, cherry blossoms in Kyoto typically bloomed between the 90th and 120th days of the year, corresponding to late March to early April.
+## Sakura Blossom in Modern Situation (1953-2019)
+@fig-1953 presents the blooming dates of sakura across Japan from 1953 to 2019( displayed in numeric form as days of the year).
+Overall data points exhibit a substantial variation.
+The red smooth trend line indicates a clear shift toward earlier blooming over time, particularly since the late 20th century, imply the influence of global warming on sakura blossom phenology.
+Notably, the clustering of most data points reflects the inherent stability of Japan's sakura blossom flowering patterns, while significant outliers, such as unusually early blooming events in recent years, may caused by the impact of extreme weather conditions or the introduction of early-blooming sakura blossom varieties.
+```{r}
+#| label: fig-1953
+#| fig-cap: "1953 to 2019 Data (Sourced from Analysis Modern Sakura Data) "
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Create the plot
+# Assuming sakura_data is your dataset
+# Prepare the data
+sakura_data$flower_date <- as.Date(sakura_data$flower_day_in_numeric, origin = paste0(sakura_data$year - 1, "-12-31"))
+
+# Create a smooth line with confidence intervals for trend
+ggplot(sakura_data, aes(x = year, y = flower_day_in_numeric)) +
+  geom_point(alpha = 0.4, color = "purple") + # Scatter points
+  geom_smooth(method = "loess", span = 0.2, color = "brown", fill = "brown", alpha = 0.3) + # Trend line with CI
+  labs(
+    title = "Sakura Flowering since 1953 to 2019",
+    x = "Year",
+    y = "Date of Flowering (Day of Year)"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12)
+  )
+```
+
+## Historical Trends in Sakura Blooming and March Temperatures (Kyoto Region)
+
+As the history_data only documents the blooming status of sakura blossoms in Kyoto, along with temperature data for March each year, we utilize these datasets in @fig-his to analyze Kyoto's blooming trends alongside its March climate conditions.
+
+The left panel illustrates that historically, sakura blossoms in Kyoto typically bloomed between the 90th and 120th days of the year, corresponding to late March to early April.
 In contrast, modern flowering days have shifted earlier, often occurring before day 100.
 
-Meanwhile, the right panel shows that for much of history, March temperatures fluctuated between 2.5°C and 10°C.
-However, in recent years, temperatures have risen sharply, now ranging from 5°C to 12°C.
-This rapid temperature increase aligns with the earlier blooming days depicted in the left panel, highlighting a clear and significant relationship between rising temperatures and cherry blossom blooming in Kyoto.
-This linkage underscores the impact of climate change on seasonal cycles and phenology.
+Meanwhile,  The right panel further illustrates that while March temperatures historically fluctuated between 2.5°C and 10°C, recent years have witnessed a sharp rise, with temperatures now ranging from 5°C to 12°C.
+The alignment between earlier blooming dates and rising temperatures underscores the influence of climate change on sakura phenology, indicating that cherry blossom flowering is a sensitive indicator of Kyoto’s warming climate.
 
@@
 #| label: fig-his
-#| fig-cap: "History and Modern"
+#| fig-cap: "History and Modern Data Comparison in Kyoto"
 #| echo: false
@@
 ## Limitation
-The model demonstrates strong predictive performance but has several limitations that should be addressed.
-By assuming that all regions respond uniformly to climate variables, the dataset may oversimplify the complex ecological processes influencing cherry blossom flowering.
-The important factors such as soil moisture variations, urban heat effects, and species-specific traits are not explicitly accounted for, potentially overlooking significant regional nuances.
-Furthermore, the absence of geographic predictors like elevation and detailed precipitation data likely contributes to larger prediction errors for outliers, particularly in regions with extreme or atypical flowering conditions.
-Additionally, the dataset does not differentiate between sakura varieties, despite substantial variation in flowering times driven by species-specific biological and environmental factors.
-This lack of certain specices may reduce the model’s precision, especially in areas with diverse sakura species and environmental contexts.
+Although the model demonstrates strong predictive performance, several limitations must be acknowledged.
+First, the assumption that all regions respond uniformly to climate variables may oversimplify the complex ecological processes that influence sakura blooming.
+This approach overlooks important microclimatic variations, such as the urban heat island effect or the unique climates of mountainous regions, which can significantly impact flowering patterns.
+
+Second, important factors like soil moisture changes, urban thermal effects, and species-specific characteristics are not explicitly included in the model.
+This omission may result in the failure to capture regional nuances, potentially exacerbating outliers in the predictions.
+Moreover, the absence of geographic predictors—such as altitude, proximity to water bodies, and detailed precipitation data—may further increase prediction errors in areas with extreme or atypical blooming conditions.
+When data availability is limited, the impact is amplified.
+
+One of the most significant limitations is the lack of distinction between sakura varieties in the dataset.
+Different varieties, such as Kawazuzakura, which blooms in early spring, and Fuyuzakura, which blooms in winter, exhibit distinct flowering patterns.
+Ignoring species-specific effects likely reduces the model’s accuracy, especially in regions with high species diversity.
+These varietal differences are essential for accurately modeling flowering times, as they reflect inherent biological and ecological variability and various species of sakura tree in each region.
 
@@
 The establishment of this prediction model will significantly enhance understanding of sakura’s sensitivity to climate, as well as inform tourism and cultural planning associated with sakura.
-Due to the influence of latitude and temperature, sakura blooms at different times across Japan, with warmer southern regions blooming earlier than cooler northern areas.
-These regional differences in flowering dates offer an opportunity to better distribute tourist influx in densely visited areas, alleviating pressure on urban infrastructure and facilities.
-Accurate predictions of flowering times can lead to more effective resource allocation, enabling tourists to plan their trips to Japan at the optimal time.
-This allows for a more tailored travel experience, with visitors enjoying sakura in different regions at different times, while simultaneously boosting regional economic development.
-Tourism bureaus can utilize these predictions to adjust event schedules, aligning activities with the expected bloom dates to provide an optimal visitor experience.
-Additionally, regional collaboration could encourage staggered travel itineraries, where tourists follow the sakura bloom progression from south to north, effectively dispersing demand across time and space.
-Northern regions with later blooming may benefit from an extended tourist season, whereas central regions such as Kyoto might face challenges with overcrowding if their peak bloom overlaps with other popular destinations.
-
-Beyond its primary function of predicting flowering times, the model incorporates precise factors such as temperature and geographic location, offering valuable insights into the ecological dynamics of sakura.
-The marked sensitivity of flowering dates to temperature underscores the characteristic responses of plant phenology to climate change, often referred to as a "natural barometer." By systematically analyzing the relationships between climate factors and flowering dates, the model reveals how sakura responds to seasonal temperature fluctuations, such as earlier blooming due to rising temperatures, as well as regional adaptations influenced by latitude.
-Furthermore, this model provides a powerful tool for evaluating the long-term impacts of climate change.
-For example, by simulating future climate scenarios under varying greenhouse gas emission trajectories, the model can predict shifts in sakura phenology over the coming decades.
-This is essential for understanding the broader implications of climate change on plant phenology, both in Japan and globally.
-Varieties with heightened sensitivity to temperature changes may face greater survival pressures as climate change intensifies, and insights from the model can guide conservation strategies, helping to identify priority regions and species that require focused protection efforts.
+Due to latitude and temperature, sakura blossoms bloom at different times across Japan, with the warmer southern regions blooming earlier than the cooler northern regions.
+These regional differences in blooming dates provide opportunities for better distribution of visitors in tourist-intensive areas, thereby reducing pressure on urban infrastructure and facilities.
+Besides, accurate prediction of bloom times allows for more efficient resource allocation, enabling visitors to plan their trips to Japan at the optimal time.
+This can provide a more targeted travel experience, where visitors can enjoy sakura blossoms in different areas at different times, while promoting regional economic development.
+Tourism boards can use these forecasts to adjust event schedules to align events with expected bloom dates to provide the best visitor experience.
+In addition, regional cooperation can encourage staggered tour schedules, where visitors can visit the sakura blossoms in the order in which they bloom from south to north, thus effectively spreading the demand over time and space.
+Northern regions that bloom later may benefit from an extended tourist season, while central regions such as Kyoto may face the challenge of overcrowding if they overlap with the peak blooming periods of other popular tourist destinations.
+
+In addition to its primary function of predicting flowering time, the model incorporates detailed factors such as temperature and geographic location, providing meaningful understanding of the ecological dynamics of sakura blossoms.
+The pronounced sensitivity of flowering date to temperature highlights the characteristic response of plant phenology to climate change, often referred to as a 'nature barometer'.
+By systematically analyzing the relationship between climatic factors and flowering dates, the model reveals how sakura blossoms respond to seasonal temperature fluctuations, such as early flowering due to warmer temperatures, as well as regional adaptations influenced by latitude.
+In addition, the model provides a powerful tool for assessing the long-term impacts of climate change.
+For example, by simulating future climate scenarios under different greenhouse gas emission trajectories, the model can predict changes in sakura blossom phenology in the coming decades.
+This is essential for understanding the broader impacts of climate change on plant phenology in Japan and globally.
+As climate change intensifies, species sensitive to temperature change may face greater pressure to survive, and understanding from the model can guide conservation strategies and help identify priority areas and species for focused conservation.
 
@@
 
-For a more precise prediction, several improvements should be implemented.
+For a more precise prediction, several improvements should be considered.
 First, incorporating additional predictors such as elevation and microclimate factors would enhance accuracy by accounting for localized influences on blooming, particularly in regions with diverse topography or urban heat effects.
 Including soil conditions and precipitation data would provide a deeper understanding of environmental factors affecting sakura phenology, especially in areas vulnerable to drought or irregular rainfall.
-Second, expanding the spatial and temporal coverage of the dataset is crucial.
+Second, expanding the spatial and temporal coverage of the dataset is importat.
 Integrating records from other sakura-growing regions, such as South Korea, China, and the United States, would enable cross-regional comparisons and distinguish universal trends from region-specific climate responses.
@@
 
-## Additional data details {#sec-sam}
-
-### Survey design and sampling techniques
-The survey design for this study integrates historical and modern sakura flowering datasets to provide a robust framework for analyzing long-term trends and regional variability.
+## Survey design and sampling techniques
+The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences.
+And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel].
 The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events.
 These reconstructions were validated against observed data starting in 1881, ensuring reliability.
-Sampling for historical data relies on curated sources from specific studies and publications, offering consistent insights into the relationship between March temperatures and flowering dates over centuries.
 
@@
 In conclusion, the historical sampling focuses on long-term climatic trends in a single location (Kyoto), while modern sampling emphasizes spatial variability and regional climate sensitivity.
-Together, these approaches enable a comprehensive analysis of how sakura flowering responds to both historical climate trends and modern regional dynamics, ensuring robust and representative findings.
+Together, these approaches enable a through analysis of how sakura flowering responds to both historical climate trends and modern regional dynamics, ensuring robust and representative findings.
+
+## Additional data details {#sec-sam}
+###History Data
+The historical dataset, shown in @fig-hissam, includes reconstructed March temperatures, the flowering day of the year (DOY), and specific flowering dates for selected years between 812 and 851 CE.
+```{r}
+#| label: fig-hissam
+#| fig-cap: "Sample Historical Sakura Data"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+# Select a sample of rows from the historical data
+sample_history_data <- history_data %>%
+  select(year, temp_c_recon, flower_doy, flower_date) %>%
+  slice(1:4)  # Select the first 4 rows for demonstration
+
+# Rename columns for better readability
+colnames(sample_history_data) <- c("Year", "Reconstructed Temp (°C)", "Day of Year (DOY)", "Flowering Date")
+
+# Display the table using kable
+kable(
+  sample_history_data,
+  col.names = c("Year", "Reconstructed Temp (°C)", "Day of Year", "Flowering Date"),
+  booktabs = TRUE,
+)
+
+```
+
+### Correlation between Each Variable
+@fig-heatmap presents the correlation heatmap for the modern sakura dataset, illustrating the relationships between key numerical variables.
+A notably strong positive correlation (close to 1) is observed between flower_day_in_numeric and full_bloom_day_in_numeric.
+Latitude and longitude also show moderate to strong positive correlations with flowering indicators, emphasizing the influence of geographic factors on blooming behavior.
+Among these, latitude exhibits a particularly strong correlation, highlighting its significance in predicting flowering dates.This is consistent with our results in @sec-result.
+And the variable year showed a weak negative correlation with flowering date, suggesting that flowering may occur earlier in the year under the influence of increasing temperatures due to global warming.
+```{r}
+#| label: fig-heatmap
+#| tbl-cap: "Correlation Heatmap"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+
+# Compute the correlation matrix
+cor_matrix <- cor(sakura_data[, sapply(sakura_data, is.numeric)], use = "complete.obs")
+
+# Convert the correlation matrix to a data frame for ggplot2
+cor_data <- as.data.frame(as.table(cor_matrix))  # Convert to long format
+cor_data <- cor_data[cor_data$Var1 != cor_data$Var2, ]  # Remove diagonal entries (self-correlation)
+
+# Plot the heatmap
+ggplot(cor_data, aes(x = Var1, y = Var2, fill = Freq)) +
+  geom_tile(color = "white", lwd = 0.7) +  # Add white borders for distinction
+  scale_fill_gradient2(
+    low = scales::alpha("#FFB7C5", 0.7),  # Sakura-inspired soft pink (low correlation)
+    mid = scales::alpha("#FFFFFF", 0.7),  # White (neutral correlation)
+    high = scales::alpha("#8B5CF6", 0.6), # Purple (high correlation)
+    midpoint = 0,
+    name = "Correlation"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 10),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    legend.position = "right"
+  ) +
+  labs(
+    title = "Correlation Heatmap of Modern Sakura Data between Variables",
+  )
+```
 
 ## Model details {#sec-model-details}
-
-## Posterior predictive check
+### Posterior predictive check
 
@@
 
-@fig-mcmc-convergence
-The MCMC diagnostics provide strong evidence of convergence and reliability in the posterior estimates.
+@fig-summary-package and @fig-mcmc-convergence collectively provide a through view of the model's performance and reliability.
+The coefficient estimates with 95% confidence intervals underscore the significant influence of latitude and month_mean_temp in predicting sakura flowering dates, while longitude appears less impact.
+@fig-mcmc-convergence perform the MCMC diagnostics provide strong evidence of convergence and reliability in the posterior estimates.
 The trace plots for key parameters, including latitude, longitude, and month_mean_temp, demonstrate good mixing across all four chains, with no discernible trends or drift over iterations.
@@
 
+```{r}
+#| label: fig-summary-package
+#| fig-cap: "Model Summary"
+#| echo: false
+#| warning: false 
+#| message: false
+#| fig-align: center
+# Load required libraries
+library(tidyverse)
+library(broom.mixed)  # For extracting Bayesian model estimates
+library(ggplot2)
+
+# Extract model estimates
+model_summary <- broom.mixed::tidy(flower_model, effects = "fixed", conf.int = TRUE)
+
+# Filter out the intercept
+model_summary <- model_summary %>% filter(term != "(Intercept)")
+
+# Create a coefficient plot
+ggplot(model_summary, aes(x = estimate, y = term)) +
+  geom_point(size = 3, color = "blue") +
+  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2, color = "black") +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
+  labs(
+    title = "Coefficient Estimates with 95% Confidence Intervals",
+    x = "Estimate",
+    y = "Predictor"
+  ) +
+  theme_minimal() +
+  theme(
+    text = element_text(size = 12),
+    plot.title = element_text(hjust = 0.5)
+  )
+
+```
+
 \newpage

### 2024-12-02 paper/paper.qmd
finish!

@@
 Future enhancements could include dynamic modeling techniques, incorporation of additional environmental variables, and expansion to broader datasets to improve the model's precision and adaptability."
-format: pdf
+format:
+  pdf:
+    fig-pos: H
 toc: true
@@
 library(broom.mixed)
+library(modelsummary)
 
@@
 For performing the analysis, we utilized several R packages.
-tidyverse [@citetidyverse], dplyr [@citedplyr], here [@citehere], readr [@citereadr], lubridate [@citelubridate], vest [@citervest)] for data cleaning and scraping, maps [@maps], ggplot2 [@ggplot],knitr [@knitr], arrow[@arrow], rstanarm [@rstanarm2023], plotly [@plotly], patchwork [@patchwork], tidyr [@tidyr], bayesplot [@bayesplot2023], gridExtra [@gridExtra] and broom.mixed [@broom] for data building and model preparation .
+tidyverse [@citetidyverse], dplyr [@citedplyr], here [@citehere], readr [@citereadr], lubridate [@citelubridate], vest [@citervest)] for data cleaning and scraping, maps [@maps], ggplot2 [@ggplot],knitr [@knitr], arrow[@arrow], rstanarm [@rstanarm2023], plotly [@plotly], patchwork [@patchwork], tidyr [@tidyr], bayesplot [@bayesplot2023], gridExtra [@gridExtra], broom.mixed [@broom], and modelsummary [@modelsummary] for data building and model preparation .
 
@@
 ## Measurement
+
 Our dataset, sourced from Alex Cookson's work [@Alex2020sakura], integrates temperature data scraped from the Japan Meteorological Agency [@Japanclimate].
@@
 ```
+
 For historical sakura data provided by Prof.
@@
 #| message: false
-
 # Generate the summary for flowering day
@@
   Statistic = names(flowering_day_summary),
-  `Flowering Day` = as.numeric(flowering_day_summary)
+  `Flowering Day` = round(as.numeric(flowering_day_summary), 2)  # Round to 2 decimal places
 )
@@
   Statistic = names(full_bloom_day_summary),
-  `Full Bloom Day` = as.numeric(full_bloom_day_summary)
+  `Full Bloom Day` = round(as.numeric(full_bloom_day_summary), 2)  # Round to 2 decimal places
 )
@@
 # Display the combined summary table
+library(knitr)
 kable(
   combined_summary_df,
-  caption = ""
 )
@@
 ## Predictor variables
+
 In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis.
@@
 ### Average Temperature of the Flowering Month
+
 The first variable is the average temperature of the flowering month (month_mean_temp).
@@
 ### Geographical Information (Latitude and Longitude)
+
 The second variable is geographical information, including latitude and longitude, which provides precise spatial details about the recording locations in different regions.
@@
 ### Years under Global Warming
+
 Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included as a random effect in the model.
@@
 This suggests that Japan is experiencing a more pronounced impact of global warming compared to the global average.
+
+More data detail could be find in @sec-sam
 
@@
 ### Latitude and Longitude with Temperature
+
 @fig-cor illustrates how temperatures vary across different locations based on their geographical coordinates.
@@
 ## Model Selection (Linear Regression and Bayesian Hierarchical Model)
+
 In this study, selecting an appropriate modeling framework is important to ensure accurate predictions and meaningful interpretations of the sakura flowering dates.
@@
 ## Model set-up
+
 This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR], with the default priors provided by rstanarm @rstanarm.
@@
 ## Result of the Analysis Data
+
 @fig-rela_result presents the correlation between each predictor variable—latitude, longitude, and monthly mean temperature—and flowering day.
@@
 ## Result of the Prediction Model
+
 ### Performance Overview Analysis
@@
 This uncertainty suggests that longitude’s influence is limited and may be mediated by other regional climatic or geographical factors.
+
 ```{r}
@@
 Together, these random effects ensure that the model accurately reflects both temporal and spatial dynamics.
+
 ```{r}
@@
 ## Interpretation
+
 Temperature is considered the most influential predictor of sakura flowering dates, with even minor increases in monthly mean temperatures significantly accelerating blooming.
@@
 ## Sakura Blossom in Modern Situation (1953-2019)
+
 @fig-1953 presents the blooming dates of sakura across Japan from 1953 to 2019( displayed in numeric form as days of the year).
@@
 ## Limitation
+
 Although the model demonstrates strong predictive performance, several limitations must be acknowledged.
@@
 ## Additional data details {#sec-sam}
-###History Data
+
+### History Data
+
 The historical dataset, shown in @fig-hissam, includes reconstructed March temperatures, the flowering day of the year (DOY), and specific flowering dates for selected years between 812 and 851 CE.
@@
 ### Correlation between Each Variable
+
 @fig-heatmap presents the correlation heatmap for the modern sakura dataset, illustrating the relationships between key numerical variables.
@@
 ## Model details {#sec-model-details}
+
 ### Posterior predictive check
 
-In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check and the distribution of posterior are show in @fig-pos-dis. 
-This shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions.
+In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check.
+The result shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions.
 The observed density, represented by the dark blue line, closely matches the predictive densities (lighter blue lines) across most of the distribution, indicating that the model captures the central tendency and major patterns effectively.
@@
 #| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
 #| fig-cap: "Examining how the model fits, and is affected by, the data"
@@
 #| message: false
-#| fig-align: center
+#| fig.pos: H
 
@@
 #| message: false
-#| fig-align: center
 

### 2024-12-03 paper/paper.qmd
Done!

@@
 
-The main outcome variables in this study are the "flowering day" and "full bloom day," which represent the specific dates (converted into numeric form) when sakura enters the flowering and full bloom stages, respectively.
+The main outcome variables in this study are the "flowering day" and "full bloom day", which represent the specific dates (converted into numeric form) when sakura enters the flowering and full bloom stages, respectively.
 A statistical summary of these variables is presented in @tbl-flower-sta, while @fig-flower depicts their overall distribution.
@@
 
-## Survey design and sampling techniques
+## Sampling, Data Observational and Potential Bias
 The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences.

### 2024-12-04 paper/paper.qmd
Done!! Congratulation

@@
 In @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, including an exploration of sakura flowering conditions from history to the present, and providing suggestions for further improvement.
-Further dataset and model details will be presented in @sec-sam and @sec-model-details separately.
+Further dataset, model details, and dataset defect will be presented in @sec-sam, @sec-model-details, and @sec-def separately.
+An idealized survey for researching Sakura flowering in the context of socio-ecological dynamics is detailed in @sec-survey.
 
@@
 
-# Appendix {#sec-app}
-
-## Sampling, Data Observational and Potential Bias
-The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences.
-And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel].
-The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events.
-These reconstructions were validated against observed data starting in 1881, ensuring reliability.
-
-But several sampling bias are not neglectble that may impact its accuracy and interpretation.
-Extreme climatic events, sakura specious, unusual flowering years can disproportionately influence the dataset, introducing outlier bias that skews trends and complicates the relationship between temperature and flowering dates.
-Additionally, the dataset's exclusive focus on Kyoto reflects selection bias, as it fails to capture regional variations in flowering patterns across Japan.
-This narrow scope, combined with the reliance on historical records from elite or literate groups, limits its broader applicability.
-
-The modern dataset, covering 1953 to 2019, uses data collected by the Japan Meteorological Agency [@Japanclimate].
-The sampling design includes a network of meteorological stations spread across Japan, capturing sakura flowering and full bloom dates from Kyushu in the south to Hokkaido in the north.
-Monthly mean air temperature data is also included to account for regional climatic variability.
-Sampling stations are geographically distributed, ensuring representation of diverse climatic zones and topographies.
-This spatially extensive design captures the progression of the sakura zensen (sakura blossom front) and provides granular insights into phenological differences across regions.Biases in how flowering dates are defined can also lead to confirmation bias, as recorded dates may reflect individual recorders' subjective definitions or expectations of what constitutes "flowering." This inconsistency can result in deviations that align more with personal or cultural interpretations than objective phenological events, further complicating the reliability of historical records.
-It is also the reason, when we build the model, we only use the data from modern_sakura_data, to ensure high accuracy and reliability for prediction.
-
-In conclusion, the historical sampling focuses on long-term climatic trends in a single location (Kyoto), while modern sampling emphasizes spatial variability and regional climate sensitivity.
-Together, these approaches enable a through analysis of how sakura flowering responds to both historical climate trends and modern regional dynamics, ensuring robust and representative findings.
-
-## Additional data details {#sec-sam}
-
-### History Data
+# Appendix {-}
+
+# Additional data details {#sec-sam}
+
+## History Data
 
@@
 
-### Correlation between Each Variable
+## Correlation between Each Variable
 
@@
 
-## Model details {#sec-model-details}
-
-### Posterior predictive check
+# Model details {#sec-model-details}
+
+## Posterior predictive check
 
@@
 
+# Sampling, Data Observational and Potential Bias {#sec-def}
+The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences.
+And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel].
+The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events.
+These reconstructions were validated against observed data starting in 1881, ensuring reliability.
+
+But several sampling bias are not neglectble that may impact its accuracy and interpretation.
+Extreme climatic events, sakura specious, unusual flowering years can disproportionately influence the dataset, introducing outlier bias that skews trends and complicates the relationship between temperature and flowering dates.
+Additionally, the dataset's exclusive focus on Kyoto reflects selection bias, as it fails to capture regional variations in flowering patterns across Japan.
+This narrow scope, combined with the reliance on historical records from elite or literate groups, limits its broader applicability.
+
+The modern dataset, covering 1953 to 2019, uses data collected by the Japan Meteorological Agency [@Japanclimate].
+The sampling design includes a network of meteorological stations spread across Japan, capturing sakura flowering and full bloom dates from Kyushu in the south to Hokkaido in the north.
+Monthly mean air temperature data is also included to account for regional climatic variability.
+Sampling stations are geographically distributed, ensuring representation of diverse climatic zones and topographies.
+This spatially extensive design captures the progression of the sakura zensen (sakura blossom front) and provides granular insights into phenological differences across regions.Biases in how flowering dates are defined can also lead to confirmation bias, as recorded dates may reflect individual recorders' subjective definitions or expectations of what constitutes "flowering." This inconsistency can result in deviations that align more with personal or cultural interpretations than objective phenological events, further complicating the reliability of historical records.
+It is also the reason, when we build the model, we only use the data from modern_sakura_data, to ensure high accuracy and reliability for prediction.
+
+In conclusion, the historical sampling focuses on long-term climatic trends in a single location (Kyoto), while modern sampling emphasizes spatial variability and regional climate sensitivity.
+Together, these approaches enable a through analysis of how sakura flowering responds to both historical climate trends and modern regional dynamics, ensuring robust and representative findings.
+
+# Idealized Methodology for Socio-Ecological Survey on Sakura Flowering {#sec-survey}
+
+## Introduction
+
+This appendix outlines an idealized survey methodology focused on public observations and opinions regarding sakura flowering patterns.
+The design prioritizes capturing data from underrepresented geographic areas in Japan, with a budget of up to $100,000.
+
+## Sampling Strategy
+
+To ensure balanced geographic representation, the survey will adopt a stratified random sampling approach focused on regions with limited historical sakura data.
+
+- **Sampling Frame**: Residents and tourists in regions across Japan, particularly areas with limited sakura flowering records.
+- **Sampling Method**: Stratified random sampling based on geographic distribution to address data gaps in underrepresented regions.
+- **Sample Size**: Target 5,000 responses, adjusted for a 10% nonresponse rate to achieve approximately 4,500 usable responses.
+- **Geographic Distribution**: Prioritize underrepresented areas (e.g., rural Hokkaido, Shikoku, and Kyushu) while maintaining coverage in major sakura observation regions like Kyoto and Tokyo.
+
+## Recruitment Plan
+
+The survey will be conducted exclusively online to maximize reach and cost efficiency:
+
+- **Online Recruitment**:
+  - Social media platforms (e.g., Instagram, X, Facebook) with region-specific campaigns targeting underrepresented areas.
+  - Advertisements on sakura and climate-related blogs and websites, as well as platforms popular among nature enthusiasts and researchers.
+  - Links to the survey hosted on platforms like Google Forms or similar secure systems.
+
+## Budget Allocation
+Online Recruitment Campaigns: $40,000        
+Participant Incentives: $20,000       
+Data Analysis and Quality Control:$15,000  
+Administrative Costs: $15,000
+
+**Total Budget**: $100,000
+
+## Survey Design
+
+The survey will focus on collecting neutral, scientifically relevant, and culturally appropriate data regarding sakura flowering patterns.
+
+- **Question Types**: Close-ended and Likert-scale questions.
+- **Response Options**: Neutral options, including “prefer not to say,” for sensitive questions.
+- **Key Topics**:
+  - Observations of sakura flowering patterns.
+  - Perceptions of changes in flowering timing.
+  - Opinions on influencing factors such as climate and geography.
+  - Awareness of the connection between sakura flowering and climate change.
+
+## Data Processing
+
+The collected data will be cleaned, weighted, and analyzed to ensure quality and reliability:
+
+1. **Prevent Duplicate Submissions**: Use unique IP tracking for online surveys.
+2. **Handle Missing Data**: Remove responses with significant missing values.
+3. **Weighting and Adjustment**: Apply equal weights for all regions to ensure balanced representation across geographic areas.
+4. **Data Validation**: Pilot the survey with 50 respondents from targeted regions to refine the questions and ensure clarity.
+
+## Example Survey Questions
+
+1. Have you observed sakura flowering in your area in the past five years?
+   - Yes
+   - No
+   - Prefer not to say
+2. What is your gender
+   - Male
+   - Femae
+   - Prefer not to say
+3. Have you noticed changes in sakura flowering dates in your region over the past decade?
+   - Yes, significantly earlier
+   - Yes, slightly earlier
+   - No noticeable change
+   - Yes, slightly later
+   - Yes, significantly later
+4. What factors do you believe most influence sakura flowering patterns?
+   - Temperature
+   - Geographic location
+   - Urban heat islands
+   - Climate change
+   - Other
+5. Do you think sakura flowering patterns are a reliable indicator of climate change?
+   - Strongly agree
+   - Agree
+   - Neutral
+   - Disagree
+   - Strongly disagree
+
+## Conclusion
+
+This survey methodology is designed to efficiently gather data about sakura flowering, with a focus on underrepresented geographic areas and public perceptions of influencing factors.
+By ensuring balanced representation and a cost-effective approach, the survey supports informed discussions on sakura flowering patterns and their broader implications, and may serves as a valuable foundation dataset for further research on socio-economic topics related to Sakura.
+
 \newpage
